---
title: "Compute the performances of the random forest stacking model,with all the elastic net predictions from all sets of brain features"
author: "Yue Wang and Narun P"
date:  "`r format(Sys.time(), '%d %b, %Y')`"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: united
    number_sections: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r load_data, echo=FALSE}
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.
```

## Note
Here we the ABCD release 4.0 data-set

# Setting up the environments

## Loading libraries
The following libraries and default settings were used during the analysis:


```{r load_libraries}
options(scipen = 999)
library("sva")
library(tidyverse)
library("tidymodels")
##parallel map

theme_set(theme_bw() + theme(panel.grid = element_blank()))
## parallel processing number of cores register
all_cores <- parallel::detectCores(logical = FALSE) - 10

doParallel::registerDoParallel(cores = all_cores)

```

## Loading paths

We first loaded all of the relevant data files (not shown here as they refer to local directories):

```{r loading_data, echo=FALSE}
# from Qnap data windows
#datafolder = "//np-qnapa/Data/ABCD/ABCD4/ABCD4SQL/"
#scriptfold = "//np-qnapa/Data/Yue script/"
#NDAfold = "//np-qnapa/Data/ABCD/ABCD4/ABCDStudyNDA/"
#utilFold = "//np-qnapa/Data/ABCD/ABCD3/Analysis/utilFunc/"
#studyNDAFold = "//np-qnapa/Data/ABCD/ABCD4/ABCDStudyNDA/"
#outputfolder = "//np-qnapa/Data/ABCD/ABCD4/ABCD4_precessed_data/"


## linux directory
#datafolder = "/media/Data/ABCD/ABCD4/ABCD4SQL/"
#scriptfold = "/media/Data/Yue script/"
#NDAfold = "/media/Data/ABCD/ABCD4/ABCDStudyNDA/"
#utilFold = "/media/Data/ABCD/ABCD3/Analysis/utilFunc/"
#studyNDAFold = "/media/Data/ABCD/ABCD4/ABCDStudyNDA/"
#outputfolder = "/media/Data/ABCD/ABCD4/ABCD4_precessed_data/"
#featurefolder = "/media/Data/ABCD/ABCD4/Analysis/ManipulatedData/"


## mac directory
datafolder = "/Volumes/Data/ABCD/ABCD4/ABCD4SQL/"
scriptfold = "/Volumes/Data/Yue script/"
NDAfold = "/Volumes/Data/ABCD/ABCD4/ABCDStudyNDA/"
utilFold = "/Volumes/Data/ABCD/ABCD3/Analysis/utilFunc/"
studyNDAFold = "/Volumes/Data/ABCD/ABCD4/ABCDStudyNDA/"
outputfolder = "/Volumes/Data/ABCD/ABCD4/ABCD4_precessed_data/"
featurefolder = "/Volumes/Data/ABCD/ABCD4/Analysis/ManipulatedData/"

source(paste0(scriptfold,"stacking_gfactor_modelling/r_functions.R"))


```

## Load the computed results


```{r}

rf_followup_list <- readRDS(paste0(scriptfold,'stacking_gfactor_modelling/collect_random_forest_results/random_forest_followup_results.RDS'))

rf_baseline_list <- readRDS(paste0(scriptfold,'stacking_gfactor_modelling/collect_random_forest_results/random_forest_baseline_results.RDS'))
## use the following code if the results are by sites
#batch_idx_vec <- seq(1:21)


#rf_baseline_list<- batch_idx_vec %>% #map(.,~readRDS(paste0(scriptfold,'stacking_gfactor_modelling/random_forest_results/random_forest_baseline.',.,'.RDS')))

### naming list if they are individually loaded
#baseline_site_list <- map(baseline_test_list, ~select(.,"SITE_ID_L")%>% unique())%>% do.call(rbind,.)
#names(baseline_test_list) <- baseline_site_list$SITE_ID_L

#names(rf_baseline_list) <- baseline_site_list$SITE_ID_L
```

# Computing the results tables


Extracted the predictions of the test data from loeaded results.

```{r}
baseline_test_list <- map(rf_baseline_list,"test_data")
baseline_test_pred <- map(rf_baseline_list,"test_pred")

followup_test_pred <- map(rf_followup_list,"test_pred")
followup_test_list <- map(rf_followup_list,"test_data")

## checking the number of observations across all sites

baseline_test_list%>% map(.,~dim(.)[1])%>% 
                  do.call(rbind,.)%>% 
                  t()%>%
                  tibble::as_tibble()%>%
    kableExtra::kbl(caption = "number of observations for all sites in baseline") %>%
    kableExtra::kable_classic(full_width = F, 
                             html_font = "Cambria")

followup_test_list%>%  map(.,~dim(.)[1])%>% 
                  do.call(rbind,.)%>% 
                  t()%>%
                  tibble::as_tibble()%>%
    kableExtra::kbl(caption = "number of observations for all sites in followup") %>%
    kableExtra::kable_classic(full_width = F, 
                             html_font = "Cambria")

```

# Compute the performance metrics and write tables.

```{r}
baseline_pred_tibble_list <- map(baseline_test_pred,"model_predict")

baseline_metrics <- map2(.x =baseline_test_list,.y=baseline_pred_tibble_list,~metric_compute_site(data_input = .y, site_input = .x))

baseline_metrics%>% 
  do.call(rbind,.)%>%
    kableExtra::kbl(caption = "metrics for all sites in baseline") %>%
    kableExtra::kable_classic(full_width = F, 
                             html_font = "Cambria")


baseline_metrics_table <- baseline_metrics%>% 
  do.call(rbind,.)

baseline_metric_avg <- average_metric_one_mod(metric_list =baseline_metrics_table)

baseline_metric_avg_table <- baseline_metric_avg %>%
  mutate_if(is.numeric, round, digits=3)%>%
  mutate("correlation (sd)" = paste0(correlation," (",cor_sd,")"))%>%
  mutate("tradrsq (sd)" = paste0(tradrsq," (",rsq_sd,")"))%>%
  mutate("MAE (sd)" = paste0(MAE," (",mae_sd,")"))%>%
  mutate("RMSE (sd)" = paste0(RMSE," (",rmse_sd,")"))%>%
  select_if(is.character)
  
avg_table_var_names <- c("correlation (sd)", "tradrsq (sd)","MAE (sd)","RMSE (sd)"  )

  baseline_metric_avg_table%>%
    dplyr::select(all_of(avg_table_var_names))%>%
    kableExtra::kbl(caption = paste0("metrics for modalities averaged across sites in baseline")) %>%
    kableExtra::kable_classic(full_width = F, 
                             html_font = "Cambria")




```


```{r}
followup_pred_tibble_list <- map(followup_test_pred,"model_predict")

followup_metrics <- map2(.x =followup_test_list,.y=followup_pred_tibble_list,~metric_compute_site(data_input = .y, site_input = .x))

followup_metrics%>% 
  do.call(rbind,.)%>%
    kableExtra::kbl(caption = "metrics for all sites in baseline") %>%
    kableExtra::kable_classic(full_width = F, 
                             html_font = "Cambria")


followup_metrics_table <- followup_metrics%>% 
  do.call(rbind,.)


followup_metric_avg <- average_metric_one_mod(metric_list =followup_metrics_table)

followup_metric_avg_table <- followup_metric_avg %>%
  mutate_if(is.numeric, round, digits=3)%>%
  mutate("correlation (sd)" = paste0(correlation," (",cor_sd,")"))%>%
  mutate("tradrsq (sd)" = paste0(tradrsq," (",rsq_sd,")"))%>%
  mutate("MAE (sd)" = paste0(MAE," (",mae_sd,")"))%>%
  mutate("RMSE (sd)" = paste0(RMSE," (",rmse_sd,")"))%>%
  select_if(is.character)
  

  followup_metric_avg_table%>%
    dplyr::select(all_of(avg_table_var_names))%>%
    kableExtra::kbl(caption = paste0("metrics for modalities averaged across sites in followup")) %>%
    kableExtra::kable_classic(full_width = F, 
                             html_font = "Cambria")




```


```{r}


baseline_metric_output_table <-  baseline_metric_avg_table %>%
                                 mutate(event = "baseline")


followup_metric_output_table <- followup_metric_avg_table %>% 
                                 mutate(event = "followup")


output_table <- bind_rows(baseline_metric_output_table,followup_metric_output_table)%>%
                mutate(modality = "Brain")
```


```{r,eval=FALSE}

saveRDS(output_table,paste0(scriptfold,'Common_psy_gene_brain_all/saved_outputs/performance_metrics/brain_performance_metric', '.RData'))

```