---
title: "Commonality analysis for genes, mental health, social demographic lifestyle developmental and sets of brain features"
author: "Yue Wang and Narun P"
date:  "`r format(Sys.time(), '%d %b, %Y')`"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: united
    number_sections: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r load_data, echo=FALSE}
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.
```

## Note
Here we the ABCD release 4.0 data-set


This file has all the linear mixed models with genes predictions as a variable. The reasons in doing this is that the number of observations in the genes data is substantially less than all the other variables. To be more specific: we have around 5,000 observations in genes data and 11,000 observations in mental health, social demographic lifestyle developmental and sets of brain features.

# Setting up the environments

## Loading libraries
The following libraries and default settings were used during the analysis:


```{r load_libraries}
options(scipen = 999)
#library("sva")
library(tidyverse)
library("tidymodels")
##parallel map
library(partR2)
library(lme4)
library(yhat)
library(ggtext)
library(ggpubr)
library(cowplot)
library(partR2)
library(lme4)
library(yhat)
library("VennDiagram")
## library to tidy up the linear mixed models
library(sjPlot)

theme_set(theme_bw() + theme(panel.grid = element_blank()))
## parallel processing number of cores register
all_cores <- parallel::detectCores(logical = FALSE) - 5

doParallel::registerDoParallel(cores = all_cores)

```

## Setting up the path

We first loaded all of the relevant data files (not shown here as they refer to local directories):

```{r loading_data, echo=FALSE}
# from Qnap data windows
#datafolder = "//np-qnapa/Data/ABCD/ABCD4/ABCD4SQL/"
#scriptfold = "//np-qnapa/Data/Yue script/"
#NDAfold = "//np-qnapa/Data/ABCD/ABCD4/ABCDStudyNDA/"
#utilFold = "//np-qnapa/Data/ABCD/ABCD3/Analysis/utilFunc/"
#studyNDAFold = "//np-qnapa/Data/ABCD/ABCD4/ABCDStudyNDA/"
#outputfolder = "//np-qnapa/Data/ABCD/ABCD4/ABCD4_precessed_data/"

### unbuntu directories

#datafolder = "/media/Data/ABCD/ABCD4/ABCD4SQL/"
#scriptfold = "/media/Data/Yue script/"
#NDAfold = "/media/Data/ABCD/ABCD4/ABCDStudyNDA/"
#utilFold = "/media/Data/ABCD/ABCD3/Analysis/utilFunc/"
#studyNDAFold = "/media/Data/ABCD/ABCD4/ABCDStudyNDA/"
#outputfolder = "/media/Data/ABCD/ABCD4/ABCD4_precessed_data/"
#featurefolder = "/media/Data/ABCD/ABCD4/Analysis/ManipulatedData/"

### mac directories
datafolder = "/Volumes/Data/ABCD/ABCD4/ABCD4SQL/"
scriptfold = "/Volumes/Data/Yue script/"
NDAfold = "/Volumes/Data/ABCD/ABCD4/ABCDStudyNDA/"
utilFold = "/Volumes/Data/ABCD/ABCD3/Analysis/utilFunc/"
studyNDAFold = "/Volumes/Data/ABCD/ABCD4/ABCDStudyNDA/"
outputfolder = "/Volumes/Data/ABCD/ABCD4/ABCD4_precessed_data/"
featurefolder = "/Volumes/Data/ABCD/ABCD4/Analysis/ManipulatedData/"

source(paste0(scriptfold,"stacking_gfactor_modelling/r_functions.R"))


```

# Data Preparation

## load fitted gfactors from brain scan and psychopathology




### load the mental health predicted results

```{r}
psy_pred <- readRDS(paste0(scriptfold,"Common_psy_gene_brain_all/saved_outputs/psychopathology_pls_pred_2.0.RData"))

```



### Load in genetics related to cognition predicted results 


```{r}

genetics_cog <- readRDS(paste0(scriptfold,'genetics_psychopathology_common_scan_all_scripts/psychopathology_cog_gene_pred_residual', '.RData'))
```

### load the computed gfactor

```{r}

gfactor_list <- readRDS(paste0(scriptfold,"genetics_psychopathology_common_scan_all_scripts/gfactor_scale_seperate.RData"))


```


## process loaded genes and mental health model predictions

Be careful with what site you choose.



```{r}

gfactor_baselie_test <- map(gfactor_list,"output_test_baseline")
gfactor_followup_test <- map(gfactor_list,"output_test_followup")


```

```{r}
subj_info <- c("SUBJECTKEY","SITE_ID_L","EVENTNAME")

```

Functions to process the loaded prediction results.

```{r}
pred_processing <- function(baseline_pred, followup_pred, baseline_table, followup_table,pred_name){
  names_vec <- c(subj_info,pred_name)
  
  baseline_subj_info <- baseline_table %>% select(all_of(subj_info))
  baseline_pred_vec <- baseline_pred %>% select(model_predict)
  baseline_output <- bind_cols(baseline_subj_info,baseline_pred_vec)
  names(baseline_output) <- names_vec
  
  followup_subj_info <- followup_table %>% select(all_of(subj_info))
  followup_pred_vec <- followup_pred %>% select(model_predict)
  followup_output <- bind_cols(followup_subj_info,followup_pred_vec)
  names(followup_output) <- names_vec

  output_all <- bind_rows(baseline_output,followup_output)
  return(list(baseline_output = baseline_output,
              followup_output = followup_output))
}




```

Combine all the subject information and prediction together and change the names.


```{r}


processed_psy_results <- pmap(list(psy_pred[["baseline_test_pred"]],
                                   psy_pred[["baseline_test_data"]],
                                  psy_pred[["followup_test_pred"]],
                                  psy_pred[["followup_test_data"]]),
                             ~pred_processing(baseline_pred=..1,
                                              followup_pred=..3, 
                                              baseline_table=..2, 
                                              followup_table=..4,
                                              pred_name="psychopathology_pls"))

```


```{r}

site_char <- names(processed_psy_results)

```

### prepocessing genetics prediction results

load in family index data


```{r, cache = FALSE, warning=FALSE}
ACS <-read_csv(paste0(datafolder,"ACSPSW03_DATA_TABLE.csv")) 
#knitr::kable(glimpse(ACS))

#race_ethnicity
#1 = White; 2 = Black; 3 = Hispanic; 4 = Asian; 5 = Other

# guardian-report relationship
# Relationship of the participant in his or her family
# 0 = single; 1 = sibling; 2 = twin; 3 = triplet
# ACS %>% count(REL_RELATIONSHIP)

ACSselected <- ACS %>% 
  select(SUBJECTKEY, EVENTNAME, SEX, INTERVIEW_AGE, RACE_ETHNICITY, 
                              REL_FAMILY_ID, ACS_RAKED_PROPENSITY_SCORE) %>%
  mutate(RACE_ETHNICITY = recode_factor(as.factor(RACE_ETHNICITY),
                `1` = "White", `2` = "Black", `3` = "Hispanic", `4` = "Asian", `5` = "Other",
                .default = "White")) %>%
  mutate(SEX = as.factor(SEX)) %>%
  mutate(REL_FAMILY_ID = as.factor(REL_FAMILY_ID))

ACSselected %>%
 filter(EVENTNAME =="baseline_year_1_arm_1") %>%
 skimr::skim()
ACSselected_baseline <- ACSselected %>%
                        filter(EVENTNAME =="baseline_year_1_arm_1")%>%
                        select(SUBJECTKEY,REL_FAMILY_ID)

ACSselected_followup <- ACSselected %>%
                        filter(EVENTNAME =="1_year_follow_up_y_arm_1")%>%
                        select(SUBJECTKEY,REL_FAMILY_ID)
```


Process the genes data.

```{r}
genetics_cog_baseline_pred <-genetics_cog[["baseline_test_pred"]]
genetics_cog_baseline_table <-genetics_cog[["baseline_test_data"]]

genetics_cog_followup_pred <- genetics_cog[["followup_test_pred"]]
genetics_cog_followup_data <- genetics_cog[["followup_test_data"]]


pred_processing_gene <- function(baseline_pred, followup_pred, baseline_table, followup_table,pred_name){
  names_vec <- c(c("SUBJECTKEY","SITE_ID_L"),pred_name)
  
  baseline_subj_info <- baseline_table %>% select(all_of(c("SUBJECTKEY","SITE_ID_L")))
  baseline_pred_vec <- baseline_pred %>% select(model_predict)
  baseline_output <- bind_cols(baseline_subj_info,baseline_pred_vec)
  names(baseline_output) <- names_vec
  
  followup_subj_info <- followup_table %>% select(all_of(c("SUBJECTKEY","SITE_ID_L")))
  followup_pred_vec <- followup_pred %>% select(model_predict)
  followup_output <- bind_cols(followup_subj_info,followup_pred_vec)
  names(followup_output) <- names_vec

  output_all <- bind_rows(baseline_output,followup_output)
  return(list(baseline_output = baseline_output,
              followup_output = followup_output))
}

processed_gene_results <- pmap(list(genetics_cog_baseline_pred,genetics_cog_baseline_table,
                                  genetics_cog_followup_pred,genetics_cog_followup_data),
                             ~pred_processing_gene(baseline_pred=..1,
                                              followup_pred=..3, 
                                              baseline_table=..2, 
                                              followup_table=..4,
                                              pred_name="gene_cog"))


```

count the total number in the genetics

```{r}

genetics_cog_baseline_tibble <- map(genetics_cog_baseline_table,~dim(.))%>%
  do.call(rbind,.)

sum(genetics_cog_baseline_tibble[,1])

### checking unique IDs

genetics_cog_baseline_ID <- map(genetics_cog_baseline_table,~unique(.[["SUBJECTKEY"]])%>%length())%>%
                            do.call(rbind,.)
sum(genetics_cog_baseline_ID)

```

Join the brain, genes, mental health and social demographic lifestyle developmental model predictions


```{r}

join_data_all <- function(site_input){
  ### join the data and drop NA
  psy_baseline_tibble <- processed_psy_results[[site_input]][["baseline_output"]]
  psy_followup_tibble <- processed_psy_results[[site_input]][["followup_output"]]
  
   gene_baseline_tibble <-processed_gene_results[[site_input]][["baseline_output"]]
  gene_followup_tibble <- processed_gene_results[[site_input]][["followup_output"]]
  
  
   baseline_psy_gene <- full_join(psy_baseline_tibble,
                                      gene_baseline_tibble, 
                                 by =c("SUBJECTKEY","SITE_ID_L" ))
  followup_psy_gene <- full_join(psy_followup_tibble,
                                      gene_followup_tibble, 
                                 by =c("SUBJECTKEY","SITE_ID_L" ))
  

  gfactor_baseline <- gfactor_baselie_test[[site_input]]
  gfactor_followup <- gfactor_followup_test[[site_input]]
  
  baseline_all <- plyr::join_all(list(baseline_psy_gene,
                                      ACSselected_baseline,gfactor_baseline), 
                                 by ="SUBJECTKEY", type = 'full')%>%
                                 drop_na()
  followup_all <- plyr::join_all(list(followup_psy_gene,
                                      ACSselected_baseline,gfactor_followup), 
                                 by ="SUBJECTKEY", type = 'full')%>%
                                 drop_na()

 output_all <- bind_rows(baseline_all,followup_all)
  
  return(list(baseline = baseline_all,
              followup=followup_all,
              all = output_all))
  
}


```


```{r}

gfactor_all <- map(.x = site_char,~join_data_all(site_input = .x))

names(gfactor_all) <- site_char

gfactor_all_baseline <- map(gfactor_all,"baseline")
gfactor_all_followup <- map(gfactor_all,"followup")
gfactor_all_baseline_followup <- map(gfactor_all,"all")

```



## Mean centering within family and within site


This script only perform the commonality analyses for the models with genetics. In genetics there are only around 5000 participants, which is much smaller than all the other models. 

Some explanation of the variables:

mental_savg: the average of mental health predictions results within each site.

mental_cws: mental health predictions centered within each site.

gene_favg: the average of gene predictions results within each family.

gene_cwf: gene predictions centered within each family (basically zeros as the data is comprised of single child in those families).

 gene_savg_favg: averaged gene_favg estimates across each site

 gene_cws_cwf: gene_favg estimates centered within each site.
 
 
 
```{r}

center_by_family_site <- function(data_input){
  
 data_input <- data_input[order(data_input$REL_FAMILY_ID),]
 count_by_family <- data_input %>% count(REL_FAMILY_ID)

 
 mean_by_family_gene <- data_input %>% group_by(REL_FAMILY_ID)%>%
                                 summarise_at(vars(gene_cog),mean)
 
 mean_vec_gene <- rep(mean_by_family_gene$gene_cog,times = count_by_family$n)
 
 data_gene  <- data_input%>%
                 mutate(gene_favg = mean_vec_gene,
                        gene_cwf = gene_cog - gene_favg)
 
 
 output_data <- data_gene %>% 
   mutate(mental_savg = mean(psychopathology_pls))%>%
    mutate(mental_cws = psychopathology_pls - mental_savg)%>% 
    mutate(gene_savg_favg = mean(gene_favg))%>%
    mutate(gene_cws_cwf = gene_cwf - gene_savg_favg)%>% 

return(output_data)
  }


centered_all_baseline <- map(gfactor_all_baseline,~center_by_family_site(data_input = .))
centered_all_followup <- map(gfactor_all_followup,~center_by_family_site(data_input = .))

```

## Scale the overall data by each variable

```{r}
gfactor_all_pred_centered_site_baseline <- centered_all_baseline%>%
                                           do.call(rbind,.)
gfactor_all_pred_centered_site_followup <- centered_all_followup%>%
                                           do.call(rbind,.)


features_not_scale <- c(subj_info, "REL_FAMILY_ID","gfactor")

features_scale <- gfactor_all_pred_centered_site_baseline %>% select(-all_of(features_not_scale))%>% colnames()
## recipe to scale the features
recipe_scale <- function(train_input=gfactor_all_pred_centered_site_baseline){
  norm_recipe <- recipe( as.formula("gfactor~."), data = train_input) %>%
    update_role(all_of(features_scale), new_role = "predictor")%>%
    update_role("gfactor", new_role = "outcome" )%>%
    # normalize numeric predictors and outcome
    step_normalize(all_numeric_predictors())
  return(norm_recipe)
}

data_all_baseline <-recipe_scale(train_input=gfactor_all_pred_centered_site_baseline) %>%
                    prep() %>%
                    juice()


data_all_followup <-recipe_scale(train_input=gfactor_all_pred_centered_site_followup) %>%
                    prep() %>%
                    juice()



```



# Commonality analysis between genes and mental health


In genetics, we do mean center within each family. Then we center within each site. Family  and site are allowed to have a random intercept which is shown in the linear mixed model.


## The commonality effect between mental health and genes.

The function to compute commonality effects:

```{r}

common_analysis_psy_gene <- function(data_input=gfactor_all_pred_centered_site_baseline){
    
 print("psy_gene_model") 
 
psy_gene_model <- lmer(gfactor ~mental_savg+mental_cws+gene_savg_favg+gene_cws_cwf+ (1|SITE_ID_L:REL_FAMILY_ID),data = data_input)
  rsq_psy_gene <- performance::r2(psy_gene_model)

  print("psy_model")
  psy_model <- lmer(gfactor ~  mental_savg+mental_cws+ (1|SITE_ID_L:REL_FAMILY_ID),data = data_input)
 rsq_psy <- performance::r2(psy_model)
  
  
    print("gene_model")
  gene_model <- lmer(gfactor ~ gene_savg_favg+gene_cws_cwf+ (1|SITE_ID_L:REL_FAMILY_ID),data = data_input)
  rsq_gene <- performance::r2(gene_model)
  
  
  
  unique_gene_margin <- rsq_psy_gene$R2_marginal-rsq_psy$R2_marginal
  
  unique_psy_margin <- rsq_psy_gene$R2_marginal-rsq_gene$R2_marginal
    
  common_psy_gene_margin <- rsq_gene$R2_marginal+rsq_psy$R2_marginal-rsq_psy_gene$R2_marginal


  unique_gene_conditional <- rsq_psy_gene$R2_conditional-rsq_psy$R2_conditional
  
  unique_psy_conditional <- rsq_psy_gene$R2_conditional-rsq_gene$R2_conditional
    
  common_psy_gene_conditional <- rsq_psy$R2_conditional+rsq_gene$R2_conditional-rsq_psy_gene$R2_conditional
  
  output_common_tibble <- tibble(variable_effects = c("unique_gene",
                                              "unique_psy",
                                              "common_psy_gene"),
                          marginal_rsq = c(unique_gene_margin,
                                              unique_psy_margin,
                                              common_psy_gene_margin),
                          conditional_rsq = c(unique_gene_conditional,
                                              unique_psy_conditional,
                                              common_psy_gene_conditional))
  output_rsq_tibble <- tibble(model_names<- c("gene",
                                              "psy",
                                              "psy_gene"),
                          marginal_rsq = c(rsq_gene$R2_marginal,
                                              rsq_psy$R2_marginal,
                                              rsq_psy_gene$R2_marginal),
                          conditional_rsq = c(rsq_gene$R2_conditional,
                                              rsq_psy$R2_conditional,
                                              rsq_psy_gene$R2_conditional))
  
  return(list(output_common_tibble=output_common_tibble,
              output_rsq_tibble=output_rsq_tibble,
              psy_gene_model=psy_gene_model,
             psy_model=psy_model,
             gene_model=gene_model))
  }


```


Compute the baseline outputs

```{r}

common_analysis_psy_gene_all <-common_analysis_psy_gene(data_input=data_all_baseline)

common_analysis_psy_gene_all$psy_gene_model_tidy%>% print()
```

```{r}
common_analysis_psy_gene_all[[1]]%>% 
    kableExtra::kbl(caption = "Commonality analysis in baseline") %>%
    kableExtra::kable_classic(full_width = F, 
                             html_font = "Cambria")

```


```{r}

common_analysis_psy_gene_all[[2]]%>% 
    kableExtra::kbl(caption = "$R^2$ metrics for all models in baseline") %>%
    kableExtra::kable_classic(full_width = F, 
                             html_font = "Cambria")

```

Compute the followup outputs

```{r}
common_analysis_psy_gene_all_followup<-common_analysis_psy_gene(data_input=data_all_followup)

```



```{r}
common_analysis_psy_gene_all_followup[[1]]%>% 
    kableExtra::kbl(caption = "Commonality analysis in followup") %>%
    kableExtra::kable_classic(full_width = F, 
                             html_font = "Cambria")

```




```{r}

common_analysis_psy_gene_all_followup[[2]]%>% 
    kableExtra::kbl(caption = "$R^2$ metrics for all models in followup") %>%
    kableExtra::kable_classic(full_width = F, 
                             html_font = "Cambria")

```







## Plotting the venn diagram

### Get the plotting labels.

Raw means the raw r-squared score.
Percent means the percent of the total r-square the variable accounted for.

```{r}

baseline_psy_gene_vec <- common_analysis_psy_gene_all[[1]]$marginal_rsq

baseline_psy_gene_vec_corrected_percent <- baseline_psy_gene_vec/common_analysis_psy_gene_all[["output_rsq_tibble"]][["marginal_rsq"]][3]*100 
baseline_psy_gene_vec_corrected_percent <- round(baseline_psy_gene_vec_corrected_percent,2)
print(baseline_psy_gene_vec_corrected_percent)

```

```{r}

baseline_psy_gene_vec_corrected_raw <- baseline_psy_gene_vec*100 
baseline_psy_gene_vec_corrected_raw <- round(baseline_psy_gene_vec_corrected_raw,2)
print(baseline_psy_gene_vec_corrected_raw)

```


```{r}

psy_gene_vec_followup <- common_analysis_psy_gene_all_followup[[1]]$marginal_rsq


psy_brain_vec_corrected_followup_percent <- psy_gene_vec_followup/common_analysis_psy_gene_all_followup[["output_rsq_tibble"]][["marginal_rsq"]][3]*100 
psy_brain_vec_corrected_followup_percent <- round(psy_brain_vec_corrected_followup_percent,2)
print(psy_brain_vec_corrected_followup_percent)


```


```{r}
psy_brain_vec_corrected_followup_raw <- psy_gene_vec_followup*100 
psy_brain_vec_corrected_followup_raw <- round(psy_brain_vec_corrected_followup_raw,1)
print(psy_brain_vec_corrected_followup_raw)

```


### venn diagram for baseline

Plot the percentage plot

```{r}
venn_plot_baseline_psy_gene_percent <- draw.pairwise.venn(
  area1 =baseline_psy_gene_vec_corrected_percent[1]+baseline_psy_gene_vec_corrected_percent[3],
  area2 = baseline_psy_gene_vec_corrected_percent[2]+baseline_psy_gene_vec_corrected_percent[3],
  cross.area  = baseline_psy_gene_vec_corrected_percent[3],
  category = c("Genes", "Mental Health"),
  fill = c("#CC79A7", "#D55E00"),
  lty = "dashed",
  cat.col = c("black", "black"),
  filename = NULL,
  cex = 2, ## label font size
  cat.cex = 2,### caption font size
  lwd = 2,
  cat.fontface = "bold",
 cat.dist = c(0.05, -0.1), # Modified
  cat.pos = c(-10, 150),# Modified
  print.mode="percent")

grid.newpage()

grid::grid.draw(venn_plot_baseline_psy_gene_percent)
#invisible(dev.off())
```


```{r}


venn_plot_baseline_psy_gene_percent_trial <- draw.pairwise.venn(
  area1 =baseline_psy_gene_vec_corrected_percent[2]+baseline_psy_gene_vec_corrected_percent[3],
  area2 = baseline_psy_gene_vec_corrected_percent[1]+baseline_psy_gene_vec_corrected_percent[3],
  cross.area  = baseline_psy_gene_vec_corrected_percent[3],
  category = c("Mental Health","Genes" ),
  fill = c("#D55E00","#CC79A7"),
  lty = "dashed",
  cat.col = c("black", "black"),
  filename = NULL,
  cex = 2, ## label font size
  cat.cex = 2,### caption font size
  lwd = 2,
  cat.fontface = "bold",
 cat.dist = c(0.05, -0.1), # Modified
  cat.pos = c(-10, 150),# Modified
  print.mode="percent")

grid.newpage()

grid::grid.draw(venn_plot_baseline_psy_gene_percent_trial)
#invisible(dev.off())
```


Plot the raw score plot.

```{r}
venn_plot_baseline_pls_gene_raw <- draw.pairwise.venn(
  area1 =baseline_psy_gene_vec_corrected_raw[1]+baseline_psy_gene_vec_corrected_raw[3],
  area2 = baseline_psy_gene_vec_corrected_raw[2]+baseline_psy_gene_vec_corrected_raw[3],
  cross.area  = baseline_psy_gene_vec_corrected_raw[3],
  category = c("Genes", "Mental Health"),
  fill = c("#CC79A7", "#D55E00"),
  lty = "dashed",
  cat.col = c("#CC79A7", "#D55E00"),
  filename = NULL,
  cex = 2, ## label font size
  cat.cex = 2,### caption font size
  lwd = 2,
  cat.fontface = "bold",
  cat.dist = c(-0.27, 0.01), # Modified
  cat.pos = c(10, 1),# Modified
  #print.mode="percent"
  )

grid.newpage()

grid::grid.draw(venn_plot_baseline_pls_gene_raw)
#invisible(dev.off())
```


```{r,fig.width=5,fig.height=2}
venn_plot_baseline_pls_gene_raw <- draw.pairwise.venn(
  area1 =baseline_psy_gene_vec_corrected_raw[1]+baseline_psy_gene_vec_corrected_raw[3],
  area2 = baseline_psy_gene_vec_corrected_raw[2]+baseline_psy_gene_vec_corrected_raw[3],
  cross.area  = baseline_psy_gene_vec_corrected_raw[3],
  category = c("Genes", "Mental Health"),
  fill = c("#CC79A7", "#D55E00"),
  lty = "dashed",
  cat.col = c("#CC79A7", "#D55E00"),
  filename = NULL,
  cex = 2, ## label font size
  cat.cex = 2,### caption font size
  lwd = 2,
  cat.fontface = "bold",
  cat.dist = c(0.05, 0.05), # Modified
  cat.pos = c(20, 1),# Modified
  scaled = FALSE
  #print.mode="percent"
  )

grid.newpage()

grid::grid.draw(venn_plot_baseline_pls_gene_raw)
#invisible(dev.off())
```


### venn diagram for followup


```{r}
venn_plot_psy_gene_followup_percent <- draw.pairwise.venn(
  area1 =psy_brain_vec_corrected_followup_percent[1]+psy_brain_vec_corrected_followup_percent[3],
  area2 = psy_brain_vec_corrected_followup_percent[2]+psy_brain_vec_corrected_followup_percent[3],
  cross.area  = psy_brain_vec_corrected_followup_percent[3],
  category = c("Genes", "Mental Health"),
  fill = c("#CC79A7", "#D55E00"),
  lty = "dashed",
  cat.col = c("black", "black"),
  filename = NULL,
  cex = 2, ## label font size
  cat.cex = 2,### caption font size
  lwd = 2,
  cat.fontface = "bold",
 cat.dist = c(0.05, -0.1), # Modified
  cat.pos = c(-10, 150),# Modified
  print.mode="percent"
  )

grid.newpage()

grid::grid.draw(venn_plot_psy_gene_followup_percent)
#invisible(dev.off())

```


```{r}
venn_plot_psy_gene_followup_raw <- draw.pairwise.venn(
  area1 =psy_brain_vec_corrected_followup_raw[1]+psy_brain_vec_corrected_followup_raw[3],
  area2 = psy_brain_vec_corrected_followup_raw[2]+psy_brain_vec_corrected_followup_raw[3],
  cross.area  = psy_brain_vec_corrected_followup_raw[3],
  category = c("Genes", "Mental Health"),
  fill = c("#CC79A7", "#D55E00"),
  lty = "dashed",
  cat.col = c("#CC79A7", "#D55E00"),
  filename = NULL,
  cex = 2, ## label font size
  cat.cex = 2,### caption font size
  lwd = 2,
  cat.fontface = "bold",
  cat.dist = c(-0.27, 0.01), # Modified
  cat.pos = c(10, 1)# Modified
  #print.mode="percent"
  )

grid.newpage()

grid::grid.draw(venn_plot_psy_gene_followup_raw)
#invisible(dev.off())

```



```{r,fig.width=5,fig.height=2}
venn_plot_psy_gene_followup_raw <- draw.pairwise.venn(
  area1 =psy_brain_vec_corrected_followup_raw[1]+psy_brain_vec_corrected_followup_raw[3],
  area2 = psy_brain_vec_corrected_followup_raw[2]+psy_brain_vec_corrected_followup_raw[3],
  cross.area  = psy_brain_vec_corrected_followup_raw[3],
  category = c("Genes", "Mental Health"),
  fill = c("#CC79A7", "#D55E00"),
  lty = "dashed",
  cat.col = c("#CC79A7", "#D55E00"),
  filename = NULL,
  cex = 2, ## label font size
  cat.cex = 2,### caption font size
  lwd = 2,
  cat.fontface = "bold",
  cat.dist = c(0.05, 0.05), # Modified
  cat.pos = c(20, 1),# Modified
  scaled = FALSE
  #print.mode="percent"
  )

grid.newpage()

grid::grid.draw(venn_plot_psy_gene_followup_raw)
#invisible(dev.off())

```

## Print mixed model output

Linear mixed models at baseline:

```{r}

### model with gene and mental health

tab_model(common_analysis_psy_gene_all$psy_gene_model,
          common_analysis_psy_gene_all$psy_model,
          common_analysis_psy_gene_all$gene_model)
```


Linear mixed models at followup

```{r}
tab_model(common_analysis_psy_gene_all_followup$psy_gene_model,
          common_analysis_psy_gene_all_followup$psy_model,
          common_analysis_psy_gene_all_followup$gene_model)
```