---
title: "Cleaning and quality control structural-mri data table"
author: "Yue Wang and Narun P"
date:  "`r format(Sys.time(), '%d %b, %Y')`"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: united
    number_sections: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## This analysis uses ABCD Release 3
starting with setting up library and script/data folders

```{r}
rm(list=ls())

library(tidyverse)



datafolder = "/media/Data/ABCD/ABCD4/ABCD4SQL/"
scriptfold = "/media/Data/Yue script/"
NDAfold = "/media/Data/ABCD/ABCD4/ABCDStudyNDA/"
utilFold = "/media/Data/ABCD/ABCD3/Analysis/utilFunc/"
studyNDAFold = "/media/Data/ABCD/ABCD4/ABCDStudyNDA/"
outputfolder = "/media/Data/ABCD/ABCD4/ABCD4_precessed_data/"
featurefolder = "/media/Data/ABCD/ABCD4/Analysis/ManipulatedData/"


```



## Load data

```{r}

sMRIAsegAparc1 <-as_tibble(read.csv(paste0(datafolder,"ABCD_SMRIP10201_DATA_TABLE.csv"))) 
sMRIAsegAparc2 <-as_tibble(read.csv(paste0(datafolder,"ABCD_SMRIP20201_DATA_TABLE.csv"))) 

MRIsMRIDest1 <-as_tibble(read.csv(paste0(datafolder,"ABCD_MRISDP10201_DATA_TABLE.csv")))
MRIsMRIDest2 <-as_tibble(read.csv(paste0(datafolder,"ABCD_MRISDP20201_DATA_TABLE.csv"))) 
## there is ABCD 4.0 file, QC according to the ABCD 4.0 instructions

QCsMRI <-tibble::as_tibble(read.table(paste0(studyNDAFold,"abcd_imgincl01.txt"),header=TRUE)) 

QCsMRI <- QCsMRI[-1,]##remove the line that explaines the variables
QCsMRI <- QCsMRI%>%
  rename(SUBJECTKEY=subjectkey,EVENTNAME=eventname,IMGINCL_T1W_INCLUDE=imgincl_t1w_include)%>%
  select(SUBJECTKEY, EVENTNAME, IMGINCL_T1W_INCLUDE)

QCsMRI %>% count(EVENTNAME,IMGINCL_T1W_INCLUDE)
```


join data 
```{r}

Screen <- plyr::join_all(list(sMRIAsegAparc1, sMRIAsegAparc2, MRIsMRIDest1, MRIsMRIDest2,QCsMRI), by=c("SUBJECTKEY", 'EVENTNAME'), type='full')

screenUniq <- Screen[,!duplicated(colnames(Screen))]

screenUniqRowID <- tibble::rowid_to_column(screenUniq, "ID")

```

only include data that IMGINCL_T1W_INCLUDE from ABCD_IMGINCL01_DATA_TABLE.csv

```{r}

screenQCExcluded <- screenUniqRowID %>%
  filter(IMGINCL_T1W_INCLUDE == 1) %>% 
  select(-IMGINCL_T1W_INCLUDE)
  
nrow(screenUniqRowID)
nrow(screenQCExcluded)
```

Load dict and change names

```{r}

#load the readable names based on dictionary
sMRIVarNames<-tbl_df(readxl::read_excel(paste0(utilFold,"sMRIVariableToImport.xlsx"))) %>% 
  select(original, CondReadableFilteredGgseg) %>% drop_na(CondReadableFilteredGgseg)

sMRIVarNames$CondReadableFilteredGgseg[1:19] <- paste0("Vol_",sMRIVarNames$CondReadableFilteredGgseg[1:19])




#change the names
sMRI.DictNames <- screenQCExcluded
for (sMRIVar in 1:nrow(sMRIVarNames)) {
  sMRI.DictNames <- sMRI.DictNames %>%
  rename(!!sMRIVarNames$CondReadableFilteredGgseg[sMRIVar] := !!sMRIVarNames$original[sMRIVar])  
}


###Destrieux ROI 


### change names of sulcal depth


roi_names <- sMRIVarNames$CondReadableFilteredGgseg[174:321]%>%
            str_remove_all("Dest_Area_")


sulcal_depth_roi_names <- paste0("Dest_Sulcal_Depth_", roi_names)

sulcal_depth_tibble <- sMRI.DictNames %>%
                       select(all_of(paste0("MRISDP_", seq(from =152, to = 299, by = 1))))


names(sulcal_depth_tibble) <- sulcal_depth_roi_names


## average T1 intensity white matter 

avg_T1_white_roi_names <- paste0("Avg_T1_White_", roi_names)

avg_T1_white_tibble <- sMRI.DictNames %>%
                       select(all_of(paste0("MRISDP_", seq(from =605, to = 752, by = 1))))


names(avg_T1_white_tibble) <- avg_T1_white_roi_names


## average T1 intensity gray matter 

avg_T1_gray_roi_names <- paste0("Avg_T1_Gray_", roi_names)

avg_T1_Gray_tibble <- sMRI.DictNames %>%
                       select(all_of(paste0("MRISDP_", seq(from =756, to = 903, by = 1))))


names(avg_T1_Gray_tibble) <- avg_T1_gray_roi_names


### normalised T1 intensity 


nom_T1_roi_names <- paste0("Normalised_T1_", roi_names)

nom_T1_tibble <- sMRI.DictNames %>%
                       select(all_of(paste0("MRISDP_", seq(from =907, to = 1054, by = 1))))


names(nom_T1_tibble) <- nom_T1_roi_names


### change names of ASEG rois

aseg_roi_names <- sMRIVarNames$CondReadableFilteredGgseg[1:19]%>%
            str_remove_all("ASEG_")


aseg_original_names <- sMRIVarNames$original[1:19]%>% 
                       str_remove_all("SMRI_VOL_SCS_")
                      
avg_T1_aseg_roi_names <- paste0("Avg_T1_ASEG_", aseg_roi_names)

aseg_original_roi_names <- paste0("SMRI_T1W_SCS_", aseg_original_names)

T1sMRIVarNames <- tibble(original = aseg_original_roi_names,CondReadableFilteredGgseg= avg_T1_aseg_roi_names)


### Average intensity of the normalized T2-weighted image 



avg_T1_aseg_tibble <- screenQCExcluded %>%
                       select(starts_with("SMRI_T1W_SCS_"))


#change the names
avg_T1_aseg_tibble_newnames <- avg_T1_aseg_tibble
for (sMRIVar in 1:nrow(T1sMRIVarNames)) {
  avg_T1_aseg_tibble_newnames <- avg_T1_aseg_tibble_newnames %>%
  rename(!!T1sMRIVarNames$CondReadableFilteredGgseg[sMRIVar] := !!T1sMRIVarNames$original[sMRIVar])  
}


avg_T1_aseg_tibble_newnames <- avg_T1_aseg_tibble_newnames%>%
                               select(starts_with("Avg_T1_ASEG_"))
  

```

prefix "ASEG_" = ASEG volume -> needed to be scaled by "intracranialVol"  
prefix "Dest_Thick_" = Destrieux Thickness -> needed to be scaled by "meanThickDest"  
prefix "Dest_Area_" = Destrieux Area -> needed to be scaled by "totalAreaDest"  
prefix "Dest_Vol_" = Destrieux volume -> needed to be scaled by "totalVolDest"

```{r}
sMRI.DictNamesWeightedVarimportant <- sMRI.DictNames %>% 
  mutate_at(vars(starts_with("Vol_ASEG_")),  ~ . / subcorticalGrayVol) %>% 
  mutate_at(vars(starts_with("Dest_Thick_")),  ~ . / meanThickDest) %>%
  mutate_at(vars(starts_with("Dest_Area_")),  ~ . / totalAreaDest) %>%
  mutate_at(vars(starts_with("Dest_Vol_")), ~. / totalVolDest) %>%
  select(SUBJECTKEY, EVENTNAME, starts_with("Vol_ASEG_"), starts_with("Dest_Thick_"), starts_with("Dest_Area_"),  starts_with("Dest_Vol_")) 



whole_Cerebellum_Cortex <- screenQCExcluded%>% select(all_of(c("SMRI_T1W_SCS_CRBCORTEXLH","SMRI_T1W_SCS_CRBCORTEXRH")))%>%
                  rowSums()

mean_vars <- screenQCExcluded%>%
            select(all_of(c("MRISDP_453","MRISDP_604","MRISDP_151","MRISDP_302",
                            "MRISDP_755","MRISDP_906","MRISDP_1057",
                            "SMRI_VOL_SCS_SUBCORTICALGV")))%>%
            rename(Dest_total_area=MRISDP_453)%>%
            rename(Dest_total_volumn=MRISDP_604)%>%
            rename(Dest_mean_thickness=MRISDP_151)%>%
            rename(Dest_mean_sulcal_depth=MRISDP_302)%>%
            rename(mean_T1_Avg_white=MRISDP_755)%>%
            rename(mean_T1_Avg_gray=MRISDP_906)%>%
            rename(mean_T1_normalised=MRISDP_1057)%>%
            rename(subcorticalgrayvolume=SMRI_VOL_SCS_SUBCORTICALGV)%>%
            mutate(Avg_T1_whole_Cerebellum_Cortex_ASEG =whole_Cerebellum_Cortex)





sMRI.T1Weighted <-do.call("cbind", list(sMRI.DictNamesWeightedVarimportant, 
                                        mean_vars, 
                                        sulcal_depth_tibble,
                                        avg_T1_white_tibble,
                                        avg_T1_Gray_tibble,
                                        nom_T1_tibble,
                                        avg_T1_aseg_tibble_newnames))


sMRI.T1Weighted <-sMRI.T1Weighted %>%
  mutate_at(vars(starts_with("Avg_T1_White_")),  ~ . / mean_T1_Avg_white)%>%
  mutate_at(vars(starts_with("Avg_T1_Gray_")),  ~ . / mean_T1_Avg_gray) %>%
  mutate_at(vars(starts_with("Normalised_T1_")),  ~ . / mean_T1_normalised) %>%
  mutate_at(vars(starts_with("Dest_Sulcal_Depth_")),  ~ . / Dest_mean_sulcal_depth)%>%
  mutate_at(vars(starts_with("Dest_Sulcal_Depth_")),  ~ . / Dest_mean_sulcal_depth) %>%
  mutate_at(vars(starts_with("Avg_T1_ASEG_")),  ~ . /Avg_T1_whole_Cerebellum_Cortex_ASEG)   



contrast_vec_cortical <- sMRI.T1Weighted%>% select(ends_with("lh_G_and_S_frontomargin"))%>%
                         colnames()%>%
                         print

contrast_vec_sub_cortical<- sMRI.T1Weighted%>% select(ends_with("Left-Cerebellum-Cortex"))%>%
                         colnames()%>%
                         print
```
for real analysis, perhaps start with "ASEG_" and "Dest_Thick_" 

write on file
```{r}
write.csv(sMRI.T1Weighted, paste0(featurefolder,"sMRI.T1Weighted.csv"))
```


