---
title: "Cleaning and quality control MID data table"
author: "Yue Wang and Narun P"
date:  "`r format(Sys.time(), '%d %b, %Y')`"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: united
    number_sections: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## This analysis uses ABCD Release 4
starting with setting up library and script/data folders

```{r}
rm(list=ls())
gc()

library(tidyverse)
#library(GPArotation)
#library(psych)



datafolder = "/media/Data/ABCD/ABCD4/ABCD4SQL/"
scriptfold = "/media/Data/Yue script/"
NDAfold = "/media/Data/ABCD/ABCD4/ABCDStudyNDA/"
utilFold = "/media/Data/ABCD/ABCD3/Analysis/utilFunc/"
studyNDAFold = "/media/Data/ABCD/ABCD4/ABCDStudyNDA/"
outputfolder = "/media/Data/ABCD/ABCD4/ABCD4_precessed_data/"
featurefolder = "/media/Data/ABCD/ABCD4/Analysis/ManipulatedData/"

```

## Load data

```{r}
MIDAseg.Beta <- tibble::as_tibble(read.csv(paste0(datafolder,"MIDAPARC03_DATA_TABLE.csv"))) 
MIDAparc.Beta <- tibble::as_tibble(read.csv(paste0(datafolder,"MIDAPARCP203_DATA_TABLE.csv"))) 
MIDDest1.Beta <- tibble::as_tibble(read.csv(paste0(datafolder,"ABCD_MIDABWDP01_DATA_TABLE.csv"))) 
MIDDest2.Beta <- tibble::as_tibble(read.csv(paste0(datafolder,"ABCD_MIDABWDP202_DATA_TABLE.csv"))) 

## column "TFMRI_MA_ACGML_B_SCS_AARH_VNDCRH" is missing!! 
##My educated guess tells me it's  TFMRI_MA_ALVSL_B_SCS_VTDCRH 

MIDAseg.Beta <- rename(MIDAseg.Beta, TFMRI_MA_ACGML_B_SCS_VNDCRH = TFMRI_MA_ALVSL_B_SCS_VTDCRH) #For renaming tibble column
```

## Prep Aseg data
make the contrast Aseg readable, remove ROIs with white matter and ventricle 

```{r}

MIDAseg.ConNames <- MIDAseg.Beta  %>%
  select(ends_with("CBWMLH")) %>%
  rename_all(~sub('CBWMLH', '', .)) %>%
  colnames()

conNames <- c("antiRewVsNeu", 
              "antiLosVsNeu", 
              "feedRewPosVsNeg", 
              "feedPunPosVsNeg", 
              "antiLargeRewVsNeu", 
              "antiSmallRewVsNeu", 
              "antiLargeRewVsSmallRew", 
              "antiLargeLossVsNeu", 
              "antiSmallLossVsNeu", 
              "antiLargeLossVsSmallLoss") 

MIDAseg.Sub <- MIDAseg.Beta %>% select('SUBJECTKEY','EVENTNAME')

ROI.FS <- MIDAseg.BetaRenamed <- list()
#take out ventricle and white matter, leaving 19 areas
for (conFSNum in 1:length(MIDAseg.ConNames)) {
  ROI.FS[conFSNum][[1]] <- MIDAseg.Beta  %>%  select(contains(MIDAseg.ConNames[conFSNum])) %>% 
    select(c(5:9, 12:14, 16:17, 22:30)) %>% colnames()
  MIDAseg.BetaRenamed[conFSNum][[1]]  <- MIDAseg.Beta  %>% 
    select('SUBJECTKEY', 'EVENTNAME', ROI.FS[conFSNum][[1]]) %>% 
    rename_at(vars(contains(MIDAseg.ConNames[conFSNum])), 
              funs(sub(MIDAseg.ConNames[conFSNum], conNames[conFSNum], .))) 
    # rename_at(vars(contains(MIDAseg.ConNames[conFSNum])), 
    #           list(~sub(MIDAseg.ConNames[conFSNum], ~conNames[conFSNum], .))) 
}

MIDAseg.BetaConRenamed <- MIDAseg.BetaRenamed %>% reduce(left_join, by = c("SUBJECTKEY","EVENTNAME"))


#change the contrast names
#MIDAseg.BetaConRenamed <- readableConMIDAsegABCD3(MIDAseg.Beta)

#load the roi names used in ggseg
asegMIDtoGGSeg3d<-tibble::as_tibble(read.csv(paste0(utilFold,"asegMIDtoGGSeg3d_19.csv")))

#change the roi names 
MIDAseg.BetaConRoiRenamed <- MIDAseg.BetaConRenamed 
for (asegROI in 1:nrow(asegMIDtoGGSeg3d)) {
  MIDAseg.BetaConRoiRenamed <- MIDAseg.BetaConRoiRenamed  %>%
  rename_all(~sub(asegMIDtoGGSeg3d$MID[asegROI], paste0("_ROI_",asegMIDtoGGSeg3d$ggseg3d[asegROI]), .))
}
```

## Prep Dest data
1) change the col names to the names in Dict
2) change the contrast names used in Dict to the same name used for Aseg
3) change the ROI names used in Dict to ggseg3d rois for plotting

```{r}
#load the readable names based on dictionary
DestName<-tibble::as_tibble(readxl::read_excel(paste0(utilFold,"MIDDestName_201.xlsx")))
DestConDictNames <- DestName %>% select("DestConOriginal","DestConReadable")

MIDDest.Beta <- plyr::join_all(list(MIDDest1.Beta, MIDDest2.Beta), by=c("SUBJECTKEY", 'EVENTNAME'), type='left')
MIDDest.BetaUniq <- MIDDest.Beta[,!duplicated(colnames(MIDDest.Beta))]

MIDDest.DictNames <- MIDDest.BetaUniq 
for (DestConROI in 1:nrow(DestConDictNames)) {
  MIDDest.DictNames <- MIDDest.DictNames  %>%
  rename(!!DestConDictNames$DestConReadable[DestConROI] := !!DestConDictNames$DestConOriginal[DestConROI])  
}

#load cont names used in ASEG 
MIDDestConToCommonCont<-tibble::as_tibble(read.csv(paste0(utilFold,"MIDDestConToCommonCont.csv")))

#change the cont names to match those in ASEG
MIDDest.DictNamesCommonCont <- MIDDest.DictNames
for (CommonCont in 1:nrow(MIDDestConToCommonCont)) {
  MIDDest.DictNamesCommonCont <- MIDDest.DictNamesCommonCont  %>%
  rename_all(~sub(MIDDestConToCommonCont$DestConReadable[CommonCont], MIDDestConToCommonCont$MidConNames[CommonCont], .))
}

#load the roi names used in ggseg
dictMIDtoGGSeg3d <-tibble::as_tibble(read.csv(paste0(utilFold,"dictMIDtoGGSeg3d.csv")))
#change the roi names 
MIDDest.GGSec3dNamesCommonCont <- MIDDest.DictNamesCommonCont
for (DestROI in 1:nrow(dictMIDtoGGSeg3d )) {
  MIDDest.GGSec3dNamesCommonCont <- MIDDest.GGSec3dNamesCommonCont  %>%
  rename_all(~sub(dictMIDtoGGSeg3d$MID[DestROI], paste0("_ROI_",dictMIDtoGGSeg3d$ggseg3d[DestROI]), .))
}

```

# Join Aseg and Dest together and export a file
```{r}
MIDDestAseg<- plyr::join_all(list(MIDAseg.BetaConRoiRenamed, MIDDest.GGSec3dNamesCommonCont), by=c("SUBJECTKEY", 'EVENTNAME'), type='left')
MIDDestAseg <- MIDDestAseg[,!duplicated(colnames(MIDDestAseg))]
#write.csv(MIDDestAseg , paste0(manipuFold,"MIDDestAsegReadableGgseg3d.csv"))
```

# testing QC based on the "one" variable
IMGINCL_MID_INCLUDE from ABCD_IMGINCL01_DATA_TABLE.csv

and provide an example of QCed data
```{r}
## there is ABCD 4.0 file, QC according to the ABCD 4.0 instructions

RecQCMID <-tibble::as_tibble(read.table(paste0(studyNDAFold,"abcd_imgincl01.txt"),header=TRUE)) 

RecQCMID <- RecQCMID[-1,]##remove the line that explaines the variables
RecQCMID <- RecQCMID%>%
  rename(SUBJECTKEY=subjectkey,EVENTNAME=eventname,IMGINCL_MID_INCLUDE=imgincl_mid_include)%>%
  select(SUBJECTKEY, EVENTNAME, IMGINCL_MID_INCLUDE)


RecQCMID%>% count(EVENTNAME,IMGINCL_MID_INCLUDE)

MIDDestAsegQCed <- plyr::join_all(list(MIDDestAseg, RecQCMID), by=c("SUBJECTKEY", 'EVENTNAME'), type='left') %>%
  filter(IMGINCL_MID_INCLUDE == 1) %>% select(-IMGINCL_MID_INCLUDE)



write.csv(MIDDestAsegQCed , paste0(featurefolder,"MIDDestAsegQCed.csv"))
  
```
