---
title: "Cleaning and quality control SST data table"
author: "Yue Wang and Narun P"
date:  "`r format(Sys.time(), '%d %b, %Y')`"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: united
    number_sections: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## This analysis uses ABCD Release 3
starting with setting up library and script/data folders

```{r}
rm(list=ls())
gc()

library(tidyverse)
#library(GPArotation)
#library(psych)


datafolder = "/media/Data/ABCD/ABCD4/ABCD4SQL/"
scriptfold = "/media/Data/Yue script/"
NDAfold = "/media/Data/ABCD/ABCD4/ABCDStudyNDA/"
utilFold = "/media/Data/ABCD/ABCD3/Analysis/utilFunc/"
studyNDAFold = "/media/Data/ABCD/ABCD4/ABCDStudyNDA/"
outputfolder = "/media/Data/ABCD/ABCD4/ABCD4_precessed_data/"
featurefolder = "/media/Data/ABCD/ABCD4/Analysis/ManipulatedData/"

```

## Load data

```{r}
SSTAsegAPac.Beta <-tibble::as_tibble(read.csv(paste0(datafolder,"MRISST02_DATA_TABLE.csv"))) 
SSTDest1.Beta <-tibble::as_tibble(read.csv(paste0(datafolder,"ABCD_TFSSTABWDP101_DATA_TABLE.csv"))) 
SSTDest2.Beta <-tibble::as_tibble(read.csv(paste0(datafolder,"ABCD_TFSSTABWDP201_DATA_TABLE.csv"))) 

```



## Prep Aseg data
make the contrast Aseg readable, remove ROIs with white matter and ventricle 

```{r}
#load the readable names based on dictionary
AName<-tbl_df(readxl::read_excel(paste0(utilFold,"SSTAsegApracName_201.xlsx")))
AConDictNames <- AName %>% select("AConOriginal","AConReadable")

SSTAsegAPac.DictNames <- SSTAsegAPac.Beta 
for (AConROI in 1:nrow(AConDictNames)) {
  SSTAsegAPac.DictNames  <- SSTAsegAPac.DictNames   %>%
  rename(!!AConDictNames$AConReadable[AConROI] := !!AConDictNames$AConOriginal[AConROI])  
}

#only include Aseg
SSTAseg.DictNames <-SSTAsegAPac.DictNames[1:230]

#take the SSTAseg and look at its prefixes for contrast names
SSTAseg.ConNames <- SSTAseg.DictNames  %>%
  select(ends_with("putamenlh")) %>%
  rename_all(~sub('putamenlh', '', .)) %>%
  colnames()

#take out ventricle and white matter, leaving 19 areas
ROI.FS <- SSTAseg.DictNamesTrimmed <- list()
for (conFSNum in 1:length(SSTAseg.ConNames)) {
  ROI.FS[conFSNum][[1]] <- SSTAseg.DictNames  %>%  select(contains(SSTAseg.ConNames[conFSNum])) %>% 
    select(c(5:9, 12:14, 16:17, 22:30)) %>% colnames()
  SSTAseg.DictNamesTrimmed[conFSNum][[1]]  <- SSTAseg.DictNames  %>% 
    select('SUBJECTKEY', 'EVENTNAME', ROI.FS[conFSNum][[1]]) 
}
SSTAseg.DictNamesTrimmedReduced <- 
  SSTAseg.DictNamesTrimmed %>% reduce(left_join, by = c("SUBJECTKEY", 'EVENTNAME'))


#load the roi names used in ggseg
asegSSTtoGGSeg3d<-tbl_df(read.csv(paste0(utilFold,"asegMIDNbacktoGGSeg3d_19.csv")))
#SST uses the same ROI name with Nback

#change the roi names 
SSTAseg.GgsegNamesTrimmedReduced <- SSTAseg.DictNamesTrimmedReduced
for (asegROI in 1:nrow(asegSSTtoGGSeg3d)) {
  SSTAseg.GgsegNamesTrimmedReduced <- SSTAseg.GgsegNamesTrimmedReduced  %>%
  rename_all(~sub(asegSSTtoGGSeg3d$NBACK[asegROI], 
                  paste0("ROI_",asegSSTtoGGSeg3d$ggseg3d[asegROI]), .))
}

```

## Prep Dest data
1) change the col names to the names in Dict
2) change the ROI names used in Dict to ggseg3d rois for plotting

```{r}

#load the readable names based on dictionary
DestName<-tbl_df(readxl::read_excel(paste0(utilFold,"SSTDestName_201.xlsx")))
DestConDictNames <- DestName %>% select("DestConOriginal","DestConReadable")

SSTDest.Beta <- plyr::join_all(list(SSTDest1.Beta, SSTDest2.Beta), by = c("SUBJECTKEY", 'EVENTNAME'), type='left')
SSTDest.BetaUniq <- SSTDest.Beta[,!duplicated(colnames(SSTDest.Beta))]

SSTDest.DictNames <- SSTDest.BetaUniq
for (DestConROI in 1:nrow(DestConDictNames)) {
  SSTDest.DictNames <- SSTDest.DictNames  %>%
  rename(!!DestConDictNames$DestConReadable[DestConROI] := !!DestConDictNames$DestConOriginal[DestConROI])  
}

#turns out SST used the same Dest  name with MID

#load the roi names used in ggseg
dictMIDtoGGSeg3d <-tbl_df(read.csv(paste0(utilFold,"dictMIDtoGGSeg3d.csv")))
#change the roi names 
SSTDest.GGSeg3dNames<- SSTDest.DictNames
for (DestROI in 1:nrow(dictMIDtoGGSeg3d )) {
  SSTDest.GGSeg3dNames <- SSTDest.GGSeg3dNames  %>%
  rename_all(~sub(dictMIDtoGGSeg3d$MID[DestROI], paste0("ROI_",dictMIDtoGGSeg3d$ggseg3d[DestROI]), .))
}

```

# Join Aseg and Dest together and export a file
```{r}
SSTDestAseg<- plyr::join_all(list(SSTAseg.GgsegNamesTrimmedReduced, SSTDest.GGSeg3dNames), 
                             by=c("SUBJECTKEY", 'EVENTNAME'), type='left')
SSTDestAseg <- SSTDestAseg[,!duplicated(colnames(SSTDestAseg))]
#write.csv(SSTDestAseg , paste0(manipuFold,"SSTDestAsegReadableGgseg3d.csv"))
```

# testing QC based on the "one" variable
IMGINCL_SST_INCLUDE from ABCD_IMGINCL01_DATA_TABLE.csv
```{r}

RecQCSST <-tibble::as_tibble(read.table(paste0(studyNDAFold,"abcd_imgincl01.txt"),header=TRUE)) 

RecQCSST <- RecQCSST[-1,]##remove the line that explaines the variables
RecQCSST <- RecQCSST%>%
  rename(SUBJECTKEY=subjectkey,EVENTNAME=eventname,IMGINCL_SST_INCLUDE=imgincl_sst_include)%>%
  select(SUBJECTKEY, EVENTNAME, IMGINCL_SST_INCLUDE)


RecQCSST %>% count(EVENTNAME,IMGINCL_SST_INCLUDE)

```

# testing QC based on behavioral flags:

from ABCD_SST02_DATA_TABLE.csv

• tfmri_sst_beh_violatorflag: Race model violators where Stop Fail RT > Go RT
• tfmri_sst_beh_glitchflag: Task coding error
• tfmri_sst_beh_0SSDcount: Number of Stop trials with 0ms SSD  

Variable names for SSRT
• tfmri_sst_all_beh_total_mssrt: Stop Signal Reaction Time, mean estimation
• tfmri_sst_all_beh_total_issrt: Stop Signal Reaction Time, integration estimation

```{r}
BehSST <-tibble::as_tibble(read.csv(paste0(datafolder,"ABCD_SST02_DATA_TABLE.csv"))) 

count(BehSST, EVENTNAME, TFMRI_SST_BEH_VIOLATORFLAG)
count(BehSST, EVENTNAME, TFMRI_SST_BEH_GLITCHFLAG)
count(BehSST, EVENTNAME, TFMRI_SST_BEH_0SSDCOUNT>1) # too many will be excluded
count(BehSST, EVENTNAME, TFMRI_SST_BEH_0SSDCOUNT>7+(1.5*(7))) # 1.5 IQR = 17.5

summary(BehSST$TFMRI_SST_BEH_0SSDCOUNT)

# BehSST %>% filter(TFMRI_SST_BEH_0SSDCOUNT>1) %>%
# ggplot(aes(x=TFMRI_SST_BEH_0SSDCOUNT, color=EVENTNAME)) + geom_histogram()
# 
# #BehSST %>% rstatix::is_outlier(TFMRI_SST_BEH_0SSDCOUNT) 
# #BehSST_0SSDCOUNTOutliers <- BehSST %>% rstatix::identify_outliers("TFMRI_SST_BEH_0SSDCOUNT") 
# 
# BehSSTQC <-tibble::as_tibble(read.csv(paste0(dataFold,"ABCD_SST02_DATA_TABLE.csv"))) %>% 
#   select(SUBJECTKEY, EVENTNAME, TFMRI_SST_BEH_VIOLATORFLAG,TFMRI_SST_BEH_GLITCHFLAG,TFMRI_SST_BEH_0SSDCOUNT)
# 
# BehSST %>% 
#   filter(TFMRI_SST_BEH_VIOLATORFLAG==0, TFMRI_SST_BEH_GLITCHFLAG==0, TFMRI_SST_BEH_PERFORMFLAG ==1) %>%
#   ggplot(aes(x=TFMRI_SST_BEH_0SSDCOUNT, color=EVENTNAME)) + geom_histogram()
# 
# BehSST %>% 
#   filter(TFMRI_SST_BEH_VIOLATORFLAG!=1, TFMRI_SST_BEH_GLITCHFLAG!=1, TFMRI_SST_BEH_PERFORMFLAG ==1) %>% 
#   count(EVENTNAME, TFMRI_SST_BEH_0SSDCOUNT>17.5)

BehSST %>% 
  filter(TFMRI_SST_BEH_VIOLATORFLAG==0, TFMRI_SST_BEH_GLITCHFLAG==0, TFMRI_SST_BEH_PERFORMFLAG ==1) %>%
  ggplot(aes(x=TFMRI_SST_ALL_BEH_TOTAL_MSSRT, color=EVENTNAME)) + geom_histogram()

BehSST %>% 
  filter(TFMRI_SST_BEH_VIOLATORFLAG!=1, TFMRI_SST_BEH_GLITCHFLAG!=1, TFMRI_SST_BEH_PERFORMFLAG ==1) %>%
  ggplot(aes(x=TFMRI_SST_ALL_BEH_TOTAL_ISSRT, color=EVENTNAME)) + geom_histogram()

# BehSST %>% 
#   filter(TFMRI_SST_BEH_VIOLATORFLAG!=1, TFMRI_SST_BEH_GLITCHFLAG!=1, TFMRI_SST_BEH_PERFORMFLAG ==1,TFMRI_SST_BEH_0SSDCOUNT<17.5) %>%
#   ggplot(aes(x=TFMRI_SST_ALL_BEH_TOTAL_MSSRT, color=EVENTNAME)) + geom_histogram()
# 
# BehSST %>% 
#   filter(TFMRI_SST_BEH_VIOLATORFLAG!=1, TFMRI_SST_BEH_GLITCHFLAG!=1, TFMRI_SST_BEH_PERFORMFLAG ==1,TFMRI_SST_BEH_0SSDCOUNT<17.5) %>%
#   ggplot(aes(x=TFMRI_SST_ALL_BEH_TOTAL_ISSRT, color=EVENTNAME)) + geom_histogram()


```

## example QC script

doesn't include tfmri_sst_beh_0SSDcount: Number of Stop trials with 0ms SSD as it will lead to too many exclusion

```{r}


BehSST <-tibble::as_tibble(read.csv(paste0(datafolder,"ABCD_SST02_DATA_TABLE.csv"))) 

SSTDestAseg_QC <- plyr::join_all(list(SSTDestAseg, RecQCSST, BehSST), by=c("SUBJECTKEY", 'EVENTNAME'), type='left') 
SSTDestAseg_QC <- SSTDestAseg_QC[,!duplicated(colnames(SSTDestAseg_QC))]

SSTDestAseg_QC %>% 
  count(EVENTNAME, IMGINCL_SST_INCLUDE == 1, TFMRI_SST_BEH_VIOLATORFLAG!=1, TFMRI_SST_BEH_GLITCHFLAG!=1)

SSTDestAsegQCed <- SSTDestAseg_QC %>%
  filter(IMGINCL_SST_INCLUDE == 1, TFMRI_SST_BEH_VIOLATORFLAG!=1, TFMRI_SST_BEH_GLITCHFLAG!=1) %>% 
  select(-IMGINCL_SST_INCLUDE,-TFMRI_SST_BEH_VIOLATORFLAG,-TFMRI_SST_BEH_GLITCHFLAG)
SSTDestAsegQCed  <- SSTDestAsegQCed[,!duplicated(colnames(SSTDestAsegQCed))]
write.csv(SSTDestAsegQCed , paste0(featurefolder,"SSTDestAsegQCed.csv"))  
                


```
