---
title: "ABCD 4.0 data Nback cleaning"
author: "Yue Wang and Narun P"
date:  "`r format(Sys.time(), '%d %b, %Y')`"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: united
    number_sections: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r load_data, echo=FALSE}
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.
```

## Note
Here we the ABCD release 4.0 data-set

## Loading libraries
The following libraries and default settings were used during the analysis:


```{r load_libraries}
options(scipen = 999)

library(tidyverse)
library("tidymodels")
##parallel map

theme_set(theme_bw() + theme(panel.grid = element_blank()))
## parallel processing number of cores register
all_cores <- parallel::detectCores(logical = FALSE) - 2
```

# Data Preparation


We first loaded all of the relevant data files (not shown here as they refer to local directories):

```{r loading_data, echo=FALSE}
# from Qnap data windows
#datafolder = "//np-qnapa/Data/ABCD/ABCD4/ABCD4SQL/"
#scriptfold = "//np-qnapa/Data/Yue script/"
#NDAfold = "//np-qnapa/Data/ABCD/ABCD4/ABCDStudyNDA/"
#utilFold = "//np-qnapa/Data/ABCD/ABCD3/Analysis/utilFunc/"
#studyNDAFold = "//np-qnapa/Data/ABCD/ABCD4/ABCDStudyNDA/"
#outputfolder = "//np-qnapa/Data/ABCD/ABCD4/ABCD4_precessed_data/"



datafolder = "/media/Data/ABCD/ABCD4/ABCD4SQL/"
scriptfold = "/media/Data/Yue script/"
NDAfold = "/media/Data/ABCD/ABCD4/ABCDStudyNDA/"
utilFold = "/media/Data/ABCD/ABCD3/Analysis/utilFunc/"
studyNDAFold = "/media/Data/ABCD/ABCD4/ABCDStudyNDA/"
outputfolder = "/media/Data/ABCD/ABCD4/Analysis/ManipulatedData/"

```

## load all of the files

The aim is to compute the following:  

 
```{r load_data2}

###loading site and scanner information
MRIinfo <-tibble::as_tibble(read.csv(paste0(datafolder, "ABCD_MRI01_DATA_TABLE.csv"))) 
Siteinfo <-tibble::as_tibble(read.csv(paste0(datafolder, "ABCD_LT01_DATA_TABLE.csv")))
MriandSite <- left_join(MRIinfo,Siteinfo, by=c('SUBJECTKEY','EVENTNAME'))
MRIinfo  %>% count(EVENTNAME,SEX)
  
###loading response variables
NIH_TB <-tibble::as_tibble(read.csv(paste0(datafolder,"ABCD_TBSS01_DATA_TABLE.csv"))) 
LittleMan <-tibble::as_tibble(read.csv(paste0(datafolder,"LMTP201_DATA_TABLE.csv"))) 
Pearson <-tibble::as_tibble(read.csv(paste0(datafolder,"ABCD_PS01_DATA_TABLE.csv"))) 
NBackBeh <- tibble::as_tibble(read.csv(paste0(datafolder, "ABCD_MRINBACK02_DATA_TABLE.csv")) ) 
Pearsonscores <- tibble::as_tibble(read.csv(paste0(datafolder, "ABCD_PS01_DATA_TABLE.csv")) ) 



###loading brain scan data (Nback only)
NBackAsegAPac.Beta <-tibble::as_tibble(read.csv(paste0(datafolder,"NBACK_BWROI02_DATA_TABLE.csv"))) 
NBackDest1.Beta <-tibble::as_tibble(read.csv(paste0(datafolder,"ABCD_TFABWDP101_DATA_TABLE.csv"))) 
NBackDest2.Beta <-tibble::as_tibble(read.csv(paste0(datafolder,"ABCD_TFABWDP201_DATA_TABLE.csv"))) 
### Note that we have not removed NA before Enet tuning to keep the most number of participants

short_names <- tibble::as_tibble(read.csv(paste0(scriptfold,"ShortNames_all.csv") ))

### load vision scan data, according to the documents some of the participants cannot see the IPad screen
vision_idx <- tibble::as_tibble(read.table(paste0(NDAfold, "abcd_svs01.txt"),header = TRUE))


```


## processing Nback data





#### Prep Aseg data
make the contrast Aseg readable, remove ROIs with white matter and ventricle 

```{r}
#load the readable names based on dictionary
AName<-tbl_df(readxl::read_excel(paste0(utilFold,"NbackAsegApracName_201.xlsx")))
AConDictNames <- AName %>% select("AConOriginal","AConReadable")

NBackAsegAPac.DictNames <- NBackAsegAPac.Beta 
for (AConROI in 1:nrow(AConDictNames)) {
  NBackAsegAPac.DictNames  <- NBackAsegAPac.DictNames   %>%
  rename(!!AConDictNames$AConReadable[AConROI] := !!AConDictNames$AConOriginal[AConROI])  
}

#only include Aseg
NBackAseg.DictNames <-NBackAsegAPac.DictNames[1:290]

#take the NBackAseg and look at its prefixes for contrast names
NBackAseg.ConNames <- NBackAseg.DictNames  %>%
  select(ends_with("putamenlh")) %>%
  rename_all(~sub('putamenlh', '', .)) %>%
  colnames()

#take out ventricle and white matter, leaving 19 areas
ROI.FS <- NBackAseg.DictNamesTrimmed <- list()

for (conFSNum in 1:length(NBackAseg.ConNames)) {
  ROI.FS[conFSNum][[1]] <- NBackAseg.DictNames  %>%  select(contains(NBackAseg.ConNames[conFSNum])) %>% 
    select(c(5:9, 12:14, 16:17, 22:30)) %>% colnames()
  NBackAseg.DictNamesTrimmed[conFSNum][[1]]  <- NBackAseg.DictNames  %>% 
    select('SUBJECTKEY', 'EVENTNAME', ROI.FS[conFSNum][[1]]) 
}
NBackAseg.DictNamesTrimmedReduced <- 
  NBackAseg.DictNamesTrimmed %>% reduce(left_join, by = c("SUBJECTKEY", 'EVENTNAME'))

#load the roi names used in ggseg
asegNBacktoGGSeg3d<-tbl_df(read.csv(paste0(utilFold,"asegMIDNBacktoGGSeg3d_19.csv")))

#change the roi names 
NBackAseg.GgsegNamesTrimmedReduced <- NBackAseg.DictNamesTrimmedReduced
for (asegROI in 1:nrow(asegNBacktoGGSeg3d)) {
  NBackAseg.GgsegNamesTrimmedReduced <- NBackAseg.GgsegNamesTrimmedReduced  %>%
  rename_all(~sub(asegNBacktoGGSeg3d$NBACK[asegROI], 
                  paste0("ROI_",asegNBacktoGGSeg3d$ggseg3d[asegROI]), .))
}

```


#### Prep Dest data
1) change the col names to the names in Dict
2) change the ROI names used in Dict to ggseg3d rois for plotting

```{r}

#load the readable names based on dictionary
DestName<-tbl_df(readxl::read_excel(paste0(utilFold,"NBACKDestName_201.xlsx")))
DestConDictNames <- DestName %>% select("DestConOriginal","DestConReadable")

NBackDest.Beta <- plyr::join_all(list(NBackDest1.Beta, NBackDest2.Beta), by= c("SUBJECTKEY", 'EVENTNAME'), type='left')
NBackDest.BetaUniq <- NBackDest.Beta[,!duplicated(colnames(NBackDest.Beta))]

NBackDest.DictNames <- NBackDest.BetaUniq
for (DestConROI in 1:nrow(DestConDictNames)) {
  NBackDest.DictNames <- NBackDest.DictNames  %>%
  rename(!!DestConDictNames$DestConReadable[DestConROI] := !!DestConDictNames$DestConOriginal[DestConROI])  
}

NBackDestConDictNames<- NBackDest.DictNames  %>%
 select(ends_with("gandsfrontomarginlh")) %>%
 rename_all(~sub('gandsfrontomarginlh', '', .)) %>%
 colnames()

#turns out Dest used the same cont name with Aseg
#NBackAseg.ConNames == NBackDestConDictNames

NBackDest.DictRoi<- NBackDest.DictNames  %>%
 select(starts_with("0back_")) %>%
 rename_all(~sub('0back_', '', .)) %>%
 colnames()

#turns out Nback used the same Dest  name with MID

#load the roi names used in ggseg
dictMIDtoGGSeg3d <-tbl_df(read.csv(paste0(utilFold,"dictMIDtoGGSeg3d.csv")))
#change the roi names 
NBackDest.GGSeg3dNames<- NBackDest.DictNames
for (DestROI in 1:nrow(dictMIDtoGGSeg3d )) {
  NBackDest.GGSeg3dNames <- NBackDest.GGSeg3dNames  %>%
 #windows
    # rename_all(~sub(dictMIDtoGGSeg3d$ï..MID[DestROI], paste0("ROI_",dictMIDtoGGSeg3d$ggseg3d[DestROI]), .))
#linux
    rename_all(~sub(dictMIDtoGGSeg3d$MID[DestROI], paste0("ROI_",dictMIDtoGGSeg3d$ggseg3d[DestROI]), .))
  }

```

### Join Aseg and Dest together and export a file
```{r}
NBackDestAseg<- plyr::join_all(list(NBackAseg.GgsegNamesTrimmedReduced, NBackDest.GGSeg3dNames), by=c("SUBJECTKEY", 'EVENTNAME'), type='left')
NBackDestAseg <- NBackDestAseg[,!duplicated(colnames(NBackDestAseg))]
```

### testing QC based on the "one" variable
IMGINCL_NBACK_INCLUDE from ABCD_IMGINCL01_DATA_TABLE.csv

and provide an example of QCed data
```{r}

## there is ABCD 4.0 file, QC according to the ABCD 4.0 instructions

RecQCNBACK <-tibble::as_tibble(read.table(paste0(studyNDAFold,"abcd_imgincl01.txt"),header=TRUE)) 

RecQCNBACK <- RecQCNBACK[-1,]##remove the line that explaines the variables
RecQCNBACK <- RecQCNBACK%>%
  rename(SUBJECTKEY=subjectkey,EVENTNAME=eventname,IMGINCL_NBACK_INCLUDE=imgincl_nback_include)%>%
  select(SUBJECTKEY, EVENTNAME, IMGINCL_NBACK_INCLUDE)

RecQCNBACK%>% count(EVENTNAME,IMGINCL_NBACK_INCLUDE)

NBackDestAsegQCed <- plyr::join_all(list(NBackDestAseg, RecQCNBACK), by=c("SUBJECTKEY", 'EVENTNAME'), type='left') %>%
  filter(IMGINCL_NBACK_INCLUDE == 1) %>% select(-IMGINCL_NBACK_INCLUDE)

```




```{r}

write.csv(NBackDestAsegQCed, paste0(outputfolder,"NBackDestAsegQCed.csv" ))

```