---
title: "Processing QCed data tables for elastic net model fitting"
author: "Yue Wang and Narun P"
date:  "`r format(Sys.time(), '%d %b, %Y')`"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: united
    number_sections: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)

options(width = 60)
local({
  hook_output <- knitr::knit_hooks$get('output')
  knitr::knit_hooks$set(output = function(x, options) {
    if (!is.null(options$max.height)) options$attr.output <- c(
      options$attr.output,
      sprintf('style="max-height: %s;"', options$max.height)
    )
    hook_output(x, options)
  })
})
```

Show part of the output if it is too long.

```{r load_data, echo=FALSE}
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.
```

## Note
Here we the ABCD release 4.0 data-set

# Setting up the environment

## Loading libraries
The following libraries and default settings were used during the analysis:


```{r load_libraries}
options(scipen = 999)
library("sva")
library(tidyverse)
library("tidymodels")
##parallel map

theme_set(theme_bw() + theme(panel.grid = element_blank()))
## parallel processing number of cores register
all_cores <- parallel::detectCores(logical = FALSE) - 10

doParallel::registerDoParallel(cores = all_cores)

```

## Setting up paths.

We first loaded all of the relevant data files (not shown here as they refer to local directories):

```{r loading_data, echo=FALSE}
# from Qnap data windows
#datafolder = "//np-qnapa/Data/ABCD/ABCD4/ABCD4SQL/"
#scriptfold = "//np-qnapa/Data/Yue script/"
#NDAfold = "//np-qnapa/Data/ABCD/ABCD4/ABCDStudyNDA/"
#utilFold = "//np-qnapa/Data/ABCD/ABCD3/Analysis/utilFunc/"
#studyNDAFold = "//np-qnapa/Data/ABCD/ABCD4/ABCDStudyNDA/"
#outputfolder = "//np-qnapa/Data/ABCD/ABCD4/ABCD4_precessed_data/"


## linux directory
#datafolder = "/media/Data/ABCD/ABCD4/ABCD4SQL/"
#scriptfold = "/media/Data/Yue script/"
#NDAfold = "/media/Data/ABCD/ABCD4/ABCDStudyNDA/"
#utilFold = "/media/Data/ABCD/ABCD3/Analysis/utilFunc/"
#studyNDAFold = "/media/Data/ABCD/ABCD4/ABCDStudyNDA/"
#outputfolder = "/media/Data/ABCD/ABCD4/ABCD4_precessed_data/"
#featurefolder = "/media/Data/ABCD/ABCD4/Analysis/ManipulatedData/"

## mac directory
datafolder = "/Volumes/Data/ABCD/ABCD4/ABCD4SQL/"
scriptfold = "/Volumes/Data/Yue script/"
NDAfold = "/Volumes/Data/ABCD/ABCD4/ABCDStudyNDA/"
utilFold = "/Volumes/Data/ABCD/ABCD3/Analysis/utilFunc/"
studyNDAFold = "/Volumes/Data/ABCD/ABCD4/ABCDStudyNDA/"
outputfolder = "/Volumes/Data/ABCD/ABCD4/ABCD4_precessed_data/"
featurefolder = "/Volumes/Data/ABCD/ABCD4/Analysis/ManipulatedData/"



```


# Data Preparation


## load all of the files

The aim is to compute almost all of the sets of all brain features into the analysis.

All of the following files are processed with quality control. Please refer to those files if necessary.


## Change the wrong site


Change the wrong site manually based on the: "Release Notes: Adolescent Brain Cognitive Development Study ℠ (ABCD Study ® ) Data Release 4.0 Changes and Known Issues"

only fixed the baseline and two year followup that is used in the analysis

As ID is required not to show in the coding shared online, please refer to this file for the exact subject IDs.


```{r}
 
Siteinfo <-tibble::as_tibble(read.csv(paste0(datafolder, "ABCD_LT01_DATA_TABLE.csv")))


Siteinfo_fixed <- Siteinfo

site_fix <- readRDS(paste0(scriptfold,'Common_psy_gene_brain_all/saved_outputs/site_fix', '.RData'))

for(i in 1:dim(site_fix)[1]){
  fix_site_id  <- site_fix$SUBJECTKEY[i]
  fix_site_event <- site_fix$EVENTNAME[i]
  fix_site <- site_fix$SITE_ID_L[i]
  Siteinfo_fixed$SITE_ID_L[which(Siteinfo_fixed$SUBJECTKEY== fix_site_id& Siteinfo_fixed$EVENTNAME == fix_site_event)] <- fix_site
}

Siteinfo <-Siteinfo_fixed 
``` 
 
 
 
```{r load_data2}

###loading site and scanner information
MRIinfo <-tibble::as_tibble(read.csv(paste0(datafolder, "ABCD_MRI01_DATA_TABLE.csv"))) 
MriandSite <- left_join(MRIinfo,Siteinfo, by=c('SUBJECTKEY','EVENTNAME'))
MRIinfo  %>% count(EVENTNAME,SEX)
  
###loading response variables
NIH_TB <-tibble::as_tibble(read.csv(paste0(datafolder,"ABCD_TBSS01_DATA_TABLE.csv"))) 
LittleMan <-tibble::as_tibble(read.csv(paste0(datafolder,"LMTP201_DATA_TABLE.csv"))) 
Pearson <-tibble::as_tibble(read.csv(paste0(datafolder,"ABCD_PS01_DATA_TABLE.csv"))) 
NBackBeh <- tibble::as_tibble(read.csv(paste0(datafolder, "ABCD_MRINBACK02_DATA_TABLE.csv")) ) 



###loading QCed brain scan data (Nback only)

NBackDestAsegQCed <- tibble::as_tibble(read.csv(paste0(featurefolder, "NBackDestAsegQCed.csv")) ) 
MIDDestAsegQCed <- tibble::as_tibble(read.csv(paste0(featurefolder, "MIDDestAsegQCed.csv")) ) 
SSTDestAsegQCed <- tibble::as_tibble(read.csv(paste0(featurefolder, "SSTDestAsegQCed.csv")) ) 



DTI_FA23Tracks <- tibble::as_tibble(read.csv(paste0(featurefolder, "DTI_FA23Tracks.csv")) ) 

RSBetNetExcludedNoCOMBATABCD4 <- tibble::as_tibble(read.csv(paste0(featurefolder, "RSBetNetExcludedNoCOMBATABCD4.csv")) ) 

dim(RSBetNetExcludedNoCOMBATABCD4)

#colnames(RSBetNetExcludedNoCOMBATABCD4)

RSBetNetExcludedNoCOMBATABCD4_selected_names <- RSBetNetExcludedNoCOMBATABCD4%>%
                                                select(-all_of(c("SUBJECTKEY","EVENTNAME" )))%>%
                                                colnames()


RSSubNetExcludedNoCOMBATedABCD4 <- tibble::as_tibble(read.csv(paste0(featurefolder, "RSSubNetExcludedNoCOMBATedABCD4.csv")) ) 

dim(RSSubNetExcludedNoCOMBATedABCD4)

RSSubNetExcludedNoCOMBATedABCD4_selected_names <- RSSubNetExcludedNoCOMBATedABCD4%>%
                                                select(-all_of(c("SUBJECTKEY","EVENTNAME" )))%>%
                                                colnames()


rsmri_variance_gordon_aseg <- tibble::as_tibble(read.csv(paste0(featurefolder, "rsmri_variance_gordon_aseg.csv")) ) 



dim(rsmri_variance_gordon_aseg)

#colnames(rsmri_variance_gordon_aseg)

sMRI.T2Weighted <- tibble::as_tibble(read.csv(paste0(featurefolder, "sMRI.T2Weighted.csv")) ) 
sMRI.T1Weighted <- tibble::as_tibble(read.csv(paste0(featurefolder, "sMRI.T1Weighted.csv")) ) 



### Note that we have not removed NA before Enet tuning to keep the most number of participants

short_names <- tibble::as_tibble(read.csv(paste0(scriptfold,"ShortNames_all.csv") ))

### load vision scan data, according to the documents some of the participants cannot see the IPad screen
vision_idx <- tibble::as_tibble(read.table(paste0(NDAfold, "abcd_svs01.txt"),header = TRUE))


```





## Join all the data sets

```{r}

vision_idx <- vision_idx[-1,]%>% mutate(SUBJECTKEY=subjectkey)%>%
                                mutate(EVENTNAME=eventname)

data_all <- plyr::join_all(list(NBackDestAsegQCed,
                                MIDDestAsegQCed,
                                SSTDestAsegQCed,
                                DTI_FA23Tracks,
                                RSBetNetExcludedNoCOMBATABCD4,
                                rsmri_variance_gordon_aseg,
                                sMRI.T2Weighted,
                                sMRI.T1Weighted,
                                NBackBeh,
                                Pearson,
                                LittleMan,
                                NIH_TB,
                                MriandSite,
                                vision_idx,
                                RSSubNetExcludedNoCOMBATedABCD4), 
                           by=c('SUBJECTKEY','EVENTNAME'), type='full')
### full join all the data sets to keep all the participants after QC. Actually smri have the most number of participants
### there are only two participants that are not in the smri data set but in other modalities.
### change integer response variables into double for later scaling and IQR
data_all$PEA_RAVLT_LD_TRIAL_VII_TC <- as.double(data_all$PEA_RAVLT_LD_TRIAL_VII_TC)
data_all$PEA_WISCV_TRS <- as.double(data_all$PEA_WISCV_TRS)
```

## filter out the participants that have problems with vision

54 subjects

```{r}
data_removed <- data_all %>% filter(snellen_va_y == 0 | snellen_va_y == 1 | vis_flg == 2)

removed_subj <- data_removed$SUBJECTKEY
data_all <- data_all %>% filter(!SUBJECTKEY %in% removed_subj)

length(removed_subj)
```


## Remove participants within the same family took measurements in different sites

### Loading Family relationship ID

```{r, cache = FALSE, warning=FALSE}
ACS <-read_csv(paste0(datafolder,"ACSPSW03_DATA_TABLE.csv")) 
#knitr::kable(glimpse(ACS))

#race_ethnicity
#1 = White; 2 = Black; 3 = Hispanic; 4 = Asian; 5 = Other

# guardian-report relationship
# Relationship of the participant in his or her family
# 0 = single; 1 = sibling; 2 = twin; 3 = triplet
# ACS %>% count(REL_RELATIONSHIP)


##event name in this file are  "baseline_year_1_arm_1"  and  "1_year_follow_up_y_arm_1"
ACSselected <- ACS %>% 
  select(SUBJECTKEY, EVENTNAME, SEX, INTERVIEW_AGE, RACE_ETHNICITY, 
                              REL_FAMILY_ID, ACS_RAKED_PROPENSITY_SCORE) %>%
  mutate(RACE_ETHNICITY = recode_factor(as.factor(RACE_ETHNICITY),
                `1` = "White", `2` = "Black", `3` = "Hispanic", `4` = "Asian", `5` = "Other",
                .default = "White")) %>%
  mutate(SEX = as.factor(SEX)) %>%
  mutate(REL_FAMILY_ID = as.factor(REL_FAMILY_ID))

ACSselected %>%
 filter(EVENTNAME =="baseline_year_1_arm_1") %>%
 skimr::skim()

```



### Remove all those participants



```{r}

data_all_trial <- left_join(data_all,ACS, by=c('SUBJECTKEY','EVENTNAME'))

# check if there are members from the same family at different sites. There are 6 of them.
data_all_trial %>%
    filter(EVENTNAME == "baseline_year_1_arm_1")%>%
  drop_na(SITE_ID_L) %>%
  filter(SITE_ID_L != "site22") %>%
  count(REL_FAMILY_ID, SITE_ID_L) %>%
  spread(SITE_ID_L, n, fill = 0) %>%
  select(-REL_FAMILY_ID) %>% 
       as.matrix %>% 
       crossprod

#below will remove those 6 
data_all_baseline <- data_all_trial %>%
  filter(EVENTNAME == "baseline_year_1_arm_1")%>%
    drop_na(SITE_ID_L) %>%
  filter(SITE_ID_L != "site22") %>%
  group_by(REL_FAMILY_ID) %>% 
  nest(SITE_ID_L, .key="SITE_ID_L") %>%
  mutate(dup = ifelse(length(c(unlist(SITE_ID_L)))==1,0,
                      ifelse(length(unique(c(unlist(SITE_ID_L)))) > 1,1,0))) %>%
  unnest(SITE_ID_L) %>%
  ungroup()

family_exclude <- unique(data_all_baseline$REL_FAMILY_ID[which(data_all_baseline$dup==1)])
 

data_all_trial <- data_all_trial%>%
                 filter(!REL_FAMILY_ID %in% family_exclude)%>%
    drop_na(SITE_ID_L) %>%
  filter(SITE_ID_L != "site22")


```


Subjects to be removed from ABCD documents named 3a. NDA 4.0 changes and known issues

```{r}
baseline_subj_remove <- readRDS(paste0(scriptfold,'Common_psy_gene_brain_all/saved_outputs/baseline_subj_remove', '.RData'))

followup_subj_remove <- readRDS(paste0(scriptfold,'Common_psy_gene_brain_all/saved_outputs/followup_subj_remove', '.RData'))

baseline_data_removed <- data_all_trial%>%
  filter(EVENTNAME == "baseline_year_1_arm_1")%>%
                 filter(!SUBJECTKEY %in% baseline_subj_remove)

followup_data_removed <- data_all_trial%>%
  filter(EVENTNAME == "2_year_follow_up_y_arm_1")%>%
                 filter(!SUBJECTKEY %in% followup_subj_remove)

data_all_trial <- rbind(baseline_data_removed,followup_data_removed)
```


## set up variable names

```{r}
TaskDVs1Batch = c("NIHTBX_PICVOCAB_UNCORRECTED", 
                  "NIHTBX_READING_UNCORRECTED",
              "NIHTBX_FLANKER_UNCORRECTED",
              "NIHTBX_PATTERN_UNCORRECTED",
              "NIHTBX_PICTURE_UNCORRECTED",
               "PEA_RAVLT_LD_TRIAL_VII_TC")


subj_info <- c('SUBJECTKEY', 'SITE_ID_L',"EVENTNAME")
```


# Set up the sets of brain features

## Getting all the contrasts

```{r}
### get the names of the contrasts for all the modalities

nback_contrasts <- NBackDestAsegQCed%>%
                   select(ends_with("Left.Cerebellum.Cortex"))%>%
                   colnames()%>%
                   str_remove_all("Left.Cerebellum.Cortex")%>%
                   print()

MID_contrasts <- MIDDestAsegQCed%>%
                   select(ends_with("Left.Cerebellum.Cortex"))%>%
                   colnames()%>%
                   str_remove_all("Left.Cerebellum.Cortex")%>%
                   print()

SST_contrasts <- SSTDestAsegQCed%>%
                   select(ends_with("Left.Cerebellum.Cortex"))%>%
                   colnames()%>%
                   str_remove_all("Left.Cerebellum.Cortex")%>%
                   print()


## "Within" and  "avg" comprise one modality

rsmri_within <- RSBetNetExcludedNoCOMBATABCD4%>%
                   select(ends_with("Auditory"))%>%
                   colnames()%>%
                   str_remove_all("Auditory")%>%
                   print()





rsmri_avg <- RSBetNetExcludedNoCOMBATABCD4%>%
                   select(ends_with("AuditoryCinguloOpercular"))%>%
                   colnames()%>%
                   str_remove_all("AuditoryCinguloOpercular")%>%
                   print()


###  "rsmri_var_gordon_ROI_" and "rsmri_var_aseg_ROI_" are one modality


rsmri_gordon <- rsmri_variance_gordon_aseg%>%
                   select(ends_with("SMhand_1"))%>%
                   colnames()%>%
                   str_remove_all("SMhand_1")%>%
                   print()


rsmri_aseg <- rsmri_variance_gordon_aseg%>%
                   select(ends_with("Left.Cerebellum.Cortex"))%>%
                   colnames()%>%
                   str_remove_all("Left.Cerebellum.Cortex")%>%
                   print()




smri_T1_aseg <- sMRI.T1Weighted%>%
                   select(ends_with("Left.Cerebellum.Cortex"))%>%
                   colnames()%>%
                   str_remove_all("Left.Cerebellum.Cortex")%>%
                   print()


smri_T2_aseg <- sMRI.T2Weighted%>%
                   select(ends_with("Left.Cerebellum.Cortex"))%>%
                   colnames()%>%
                   str_remove_all("Left.Cerebellum.Cortex")%>%
                   print()


smri_T1_dest <- sMRI.T1Weighted%>%
                   select(ends_with("lh_G_and_S_paracentral"))%>%
                   colnames()%>%
                   str_remove_all("lh_G_and_S_paracentral")%>%
                   print()


smri_T2_dest <- sMRI.T2Weighted%>%
                   select(ends_with("lh_G_and_S_paracentral"))%>%
                   colnames()%>%
                   str_remove_all("lh_G_and_S_paracentral")%>%
                   print()


smri_T1_mean_total <- c('Dest_total_area','Dest_total_volumn','Dest_mean_thickness','Dest_mean_sulcal_depth','mean_T1_Avg_white','mean_T1_Avg_gray','mean_T1_normalised','subcorticalgrayvolume','Avg_T1_whole_Cerebellum_Cortex_ASEG' )
  
  
smri_T2_mean_total <- c('mean_T2_Avg_white','mean_T2_Avg_gray','mean_T2_normalised','Avg_T2_whole_Cerebellum_Cortex_ASEG' )

```


## split all the data tables based on the contrasts


```{r}
one_contrast_extract <- function(name_input ){
 data_output = select(data_all_trial, starts_with(name_input),all_of(subj_info))
 return(data_output)
}
nback_list <- nback_contrasts %>% map(., ~one_contrast_extract(name_input = .))

MID_list <-    MID_contrasts%>% map(., ~one_contrast_extract(name_input = .))

SST_list <- SST_contrasts %>% map(., ~one_contrast_extract(name_input = .))

cog_data <- select(data_all_trial,all_of(TaskDVs1Batch),all_of(subj_info))

rsmri_within_avg_data <- select(data_all_trial,all_of(RSBetNetExcludedNoCOMBATABCD4_selected_names), all_of(subj_info))

rsmri_gordon_aseg_data <- select(data_all_trial,starts_with(rsmri_gordon),starts_with(rsmri_aseg), all_of(subj_info))

rsmri_subnet <- select(data_all_trial,all_of(RSSubNetExcludedNoCOMBATedABCD4_selected_names), all_of(subj_info))


smri_T1_aseg_list <- smri_T1_aseg %>% map(., ~one_contrast_extract(name_input = .))

smri_T2_aseg_list <- smri_T2_aseg %>% map(., ~one_contrast_extract(name_input = .))

smri_T1_dest_list <- smri_T1_dest %>% map(., ~one_contrast_extract(name_input = .))

smri_T2_dest_list <- smri_T2_dest %>% map(., ~one_contrast_extract(name_input = .))

smri_T1_mean_total_data <- select(data_all_trial,starts_with(smri_T1_mean_total), all_of(subj_info))

smri_T2_mean_total_data <- select(data_all_trial,starts_with(smri_T2_mean_total), all_of(subj_info))


##### processing DTI data

DTI_select <- DTI_FA23Tracks %>% select(starts_with("FA_"), all_of(c("EVENTNAME","SUBJECTKEY")))

suj_info_tibble <- data_all_trial %>% select(all_of(subj_info))

DTI_data <- left_join(DTI_select,suj_info_tibble,by = c("EVENTNAME","SUBJECTKEY"))





```


## Saving up all the outputs

```{r,eval=FALSE,echo=FALSE}
### all the recipes are uploaded to Nesi
###tuning hyper-parameters are done on nesi

map2(.x = nback_contrasts, .y = nback_list, ~saveRDS(.y, 
                                    paste0(scriptfold,'stacking_gfactor_modelling/data/',.x,'.RDS')))

map2(.x = MID_contrasts, .y = MID_list, ~saveRDS(.y, 
                          paste0(scriptfold,'stacking_gfactor_modelling/data/',.x , '.RDS')))

map2(.x = SST_contrasts, .y = SST_list, ~saveRDS(.y, 
                          paste0(scriptfold,'stacking_gfactor_modelling/data/',.x , '.RDS')))

saveRDS(cog_data, paste0(scriptfold,'stacking_gfactor_modelling/data/cog_data.RDS'))

saveRDS(rsmri_within_avg_data, paste0(scriptfold,'stacking_gfactor_modelling/data/rsmri_within_avg_data.RDS'))

saveRDS(rsmri_gordon_aseg_data, paste0(scriptfold,'stacking_gfactor_modelling/data/rsmri_gordon_aseg_data.RDS'))

saveRDS(rsmri_subnet, paste0(scriptfold,'stacking_gfactor_modelling/data/rsmri_subnet.RDS'))



map2(.x = smri_T1_aseg, .y = smri_T1_aseg_list, ~saveRDS(.y, 
                          paste0(scriptfold,'stacking_gfactor_modelling/data/',.x , '.RDS')))
map2(.x = smri_T2_aseg, .y = smri_T2_aseg_list, ~saveRDS(.y, 
                          paste0(scriptfold,'stacking_gfactor_modelling/data/',.x , '.RDS')))
map2(.x = smri_T1_dest, .y = smri_T1_dest_list, ~saveRDS(.y, 
                          paste0(scriptfold,'stacking_gfactor_modelling/data/',.x , '.RDS')))
map2(.x = smri_T2_dest, .y = smri_T2_dest_list, ~saveRDS(.y, 
                          paste0(scriptfold,'stacking_gfactor_modelling/data/',.x , '.RDS')))



saveRDS(smri_T1_mean_total_data, paste0(scriptfold,'stacking_gfactor_modelling/data/smri_T1_mean_total_data.RDS'))

saveRDS(smri_T2_mean_total_data, paste0(scriptfold,'stacking_gfactor_modelling/data/smri_T2_mean_total_data.RDS'))
saveRDS(DTI_data, paste0(scriptfold,'stacking_gfactor_modelling/data/DTI_data.RDS'))

```

## print out the feature names for each modality


```{r}
feature_name_print <- function(data_input){
  col_names <- data_input %>% select(-all_of(subj_info))%>% colnames()
  print(col_names)
}


map(nback_list,~feature_name_print(data_input = .))

map(MID_list,~feature_name_print(data_input = .))


map(SST_list,~feature_name_print(data_input = .))


feature_name_print(data_input =rsmri_within_avg_data)

feature_name_print(data_input =rsmri_gordon_aseg_data)

feature_name_print(data_input =rsmri_subnet)

map(smri_T1_aseg_list,~feature_name_print(data_input = .))


map(smri_T2_aseg_list,~feature_name_print(data_input = .))


map(smri_T1_dest_list,~feature_name_print(data_input = .))


map(smri_T2_dest_list,~feature_name_print(data_input = .))

feature_name_print(data_input =smri_T1_mean_total_data)
feature_name_print(data_input =smri_T2_mean_total_data)
feature_name_print(data_input =DTI_data)



```





```{r}


rsmri_gordon_aseg_trial <- readRDS(paste0(scriptfold,'stacking_gfactor_modelling/data/rsmri_gordon_aseg_data.RDS'))


```



